---
title: "Netherlands Bird Migration Map"
subtitle: "Based on weather radar measurements"
author: Bart Hoekstra
#output: html_notebook
---

```{r setup, message=FALSE, warning=TRUE, include=FALSE}
library(tidyverse)
library(bioRad)
library(suncalc)
library(terra)
library(tidyterra)
library(raster)
library(sf)
library(stars)
library(parallel)
library(ggdark)
library(ggblend)
library(spatialEco)
library(fields)
library(ggnewscale)
library(colorspace)
library(ggspatial)
library(ggpattern)
library(ggfx)
library(gghalves)
library(pbmcapply)
library(legendry)
library(skimr)
library(ggrepel)
library(cowplot)
options(ggpattern_use_R4.1_masks = TRUE)
```

# Gathering data from peak nights
## Identifying peak nights
We start with loading a dataset containing cumulative passage metrics for day and night across Dutch weather radars, both seasons and all years.

```{r}
vp_mtr <- read_csv("data/vp_mtr_ordered_seasonal_day_night_migration.csv",
  col_types = cols(
    date_trunc = col_datetime(), odim_code = col_character(), year_season = col_character(), year = col_double(),
    season = col_character(), day_night = col_character(), slope_max = col_double(), slope_max_time = col_datetime(),
    mtr = col_double(), prop = col_double(), mtr_cum = col_double(), prop_cum = col_double(), top = col_double()
  )
) %>% 
  filter(day_night == "night")

head(vp_mtr %>% dplyr::select(date_trunc, odim_code, year, season, prop_cum, top), 10)
```
The dataset is sorted from largest night to smalles night in terms of cumulative passage, so we can select the peak nights that capture 50% of migration by selecting all nights that cumulatively have selected less and then the first night that pushes it above 50%.

```{r}
vp_mtr_cum50 <- vp_mtr %>%
  filter(prop_cum < 0.5 | (lag(prop_cum) < 0.5 & prop_cum >= 0.5))

vp_mtr_cum50
```

Now that we have identified the nights, we can calculate the moment of sunset, to find the polar volume scan closest to 2.5hrs after sunset.

```{r}
calculate_scantime <- function(r, hr = 2, m = 30) {
  if (r["odim_code"] == "nlhrw") {
    lat <- 51.8371
    lon <- 5.138
  }
  if (r["odim_code"] == "nldhl") {
    lat <- 52.9528
    lon <- 4.79061
  }
  
  if (r["day_night"] == "night") {
    scantime <- suncalc::getSunlightTimes(lat = lat, lon = lon, date = as.Date(r["date_trunc"]) - 1, keep = "sunset")
    scantime <- scantime$sunset + hours(hr) + minutes(m)
  }

  scantime <- round_date(scantime, "5 mins")
}

scantimes_std <- as_datetime(unlist(apply(vp_mtr_cum50, MARGIN = 1, FUN = calculate_scantime, simplify = FALSE)))
scantimes_4hr <- as_datetime(unlist(apply(vp_mtr_cum50, MARGIN = 1, FUN = calculate_scantime, hr = 4, m = 0, simplify = FALSE)))

vp_mtr_cum50$`2h30m` <- scantimes_std
vp_mtr_cum50$`4h00m` <- scantimes_4hr
vp_mtr_cum50 %>%
  pivot_longer(cols = c(`2h30m`, `4h00m`), names_to = "momenttype", values_to = "moment") -> vp_mtr_cum50
```
## Download peak time scans
From the `moment` column in the `vp_mtr_cum50` dataframe, one can distill which pvol files have to be downloaded from the KNMI weather radar repository. At the UvA, we host those publicly available datasets locally on a private [minio](https://min.io) S3 server, but others can download the polar volume files from the KNMI directly: [Herwijnen](https://dataplatform.knmi.nl/dataset/radar-tar-vol-full-herwijnen-1-0) and [Den Helder](https://dataplatform.knmi.nl/dataset/radar-tar-volume-denhelder-1-0) after [registering](https://developer.dataplatform.knmi.nl) for a free API key.

```{r eval=FALSE, include=FALSE}
# minio/pvol/NL/HRW/2016/08/31/NLHRW_pvol_20160831T2350_6356.h5
dts <- dplyr::select(vp_mtr_cum50, odim_code, moment)

dts_hrw <- dts %>%
  filter(odim_code == "nlhrw") %>%
  pull(moment)

filepaths_hrw <- paste0(
  "minio/pvol/NL/HRW/", year(dts_hrw), "/", sprintf("%02d", month(dts_hrw)), "/", sprintf("%02d", day(dts_hrw)), "/",
  "NLHRW_pvol_", format(dts_hrw, format = "%Y%m%dT%H%M"), "_6356.h5"
)
filepaths_hrw_alt <- paste0(
  "minio/pvol/NL/HRW/", year(dts_hrw), "/", sprintf("%02d", month(dts_hrw)), "/", sprintf("%02d", day(dts_hrw)), "/",
  "NLHRW_pvol_", format(dts_hrw, format = "%Y%m%dT%H%M"), "_NL52.h5"
)
paths <- list(paste0("mc cp ", filepaths_hrw, " ."), paste0("mc cp ", filepaths_hrw_alt, " ."))

write_lines(unlist(paths), file = "data/pvol/hrw_files.sh", )

dts_dhl <- dts %>%
  filter(odim_code == "nldhl") %>%
  pull(moment)

filepaths_dhl <- paste0(
  "minio/pvol/NL/DHL/", year(dts_dhl), "/", sprintf("%02d", month(dts_dhl)), "/", sprintf("%02d", day(dts_dhl)), "/",
  "NLDHL_pvol_", format(dts_dhl, format = "%Y%m%dT%H%M"), "_6234.h5"
)
filepaths_dhl_alt <- paste0(
  "minio/pvol/NL/DHL/", year(dts_dhl), "/", sprintf("%02d", month(dts_dhl)), "/", sprintf("%02d", day(dts_dhl)), "/",
  "NLDHL_pvol_", format(dts_dhl, format = "%Y%m%dT%H%M"), "_NL51.h5"
)
paths <- list(paste0("mc cp ", filepaths_dhl, " ."), paste0("mc cp ", filepaths_dhl_alt, " ."))

write_lines(unlist(paths), file = "data/pvol/dhl_files.sh", )
```

```{r eval=FALSE, include=FALSE}
downloaded_files <- list.files("data/pvol", full.names = TRUE)
downloaded_files <- downloaded_files[!downloaded_files %in% c("data/pvol/dhl_files.sh", "data/pvol/hrw_files.sh")]
downloaded_files_hrw <- downloaded_files[str_detect(downloaded_files, "NLHRW")]
downloaded_files_dhl <- downloaded_files[str_detect(downloaded_files, "NLDHL")]

downloaded_files_dhl_dts <- as_datetime(unlist(
  lapply(downloaded_files_dhl, function(x) parse_date_time(str_split(x, "_")[[1]][3], "YmdHM"))
))
downloaded_files_hrw_dts <- as_datetime(unlist(
  lapply(downloaded_files_hrw, function(x) parse_date_time(str_split(x, "_")[[1]][3], "YmdHM"))
))

downloaded_dts_dhl <- data.frame(pvolfile = downloaded_files_dhl, moment = downloaded_files_dhl_dts)
downloaded_dts_dhl$odim_code <- "nldhl"
downloaded_dts_hrw <- data.frame(pvolfile = downloaded_files_hrw, moment = downloaded_files_hrw_dts)
downloaded_dts_hrw$odim_code <- "nlhrw"
downloaded_dts <- bind_rows(downloaded_dts_dhl, downloaded_dts_hrw)

vp_mtr_cum50 %>%
  left_join(downloaded_dts, by = join_by(odim_code == odim_code, moment == moment)) %>%
  drop_na() -> vp_mtr_cum50
```

# Process RBCs for bird density maps
The pipeline used to convert the polar volume scans to range-bias corrected PPIs that we can incorporate in our bird migration maps, is self-contained in the `rbc_preprocessing.R` file.

## RBC selection
After processing the RBCs, there is a folder `data/rbc_png/full` that contains .png's with several diagnostic plots of the processed RBCs. These have to be manually screened for clutter from rain and anomalous propagation and files should be moved to the subfolders `Accepted` if the scans are clean examples of bird migration and `Rejected` if they aren't.

## Selected usable scans
We now add the outcome of the screening procedure to the dataframe containing an overview of our data.

```{r}
accepted_files <- list.files("data/rbc_png/full/Accepted/")
rejected_files <- list.files("data/rbc_png/full/Rejected/")

rbc_file_from_png <- function(file, azim_method = "full") {
  f <- basename(file)
  ss <- str_split(f, "_")[[1]][1:4]
  radar <- str_to_lower(ss[1])
  moment <- parse_date_time(ss[3], "%Y%m%dT%H%M", exact = TRUE)
  fp <- paste0("data/rbc/", str_c(ss, collapse = "_"), "_", azim_method, ".RDS")
  return(list("odim_code" = radar, "moment" = moment, "rbcfile" = fp))
}

accepted <- bind_rows(lapply(accepted_files, rbc_file_from_png)) %>% mutate(status = "Accepted")
rejected <- bind_rows(lapply(rejected_files, rbc_file_from_png)) %>% mutate(status = "Rejected")

classified_moments <- bind_rows(accepted, rejected)

vp_mtr_cum50 %>%
  left_join(classified_moments, by = join_by(odim_code, moment)) %>%
  mutate(status = replace_na(status, "Rejected")) %>%
  drop_na() %>%
  identity() -> vp_mtr_cum50_cl
```

```{r}
vp_mtr_cum50_cl %>% filter(momenttype == "2h30m") %>% nrow()
vp_mtr_cum50_cl %>% filter(momenttype == "2h30m") %>% pull(status) %>% table()
vp_mtr_cum50_cl %>% filter(momenttype == "2h30m", status == "Rejected") %>% pull(season) %>% table()
```


## Seasonal proportion of migration covered

Having screened the scans now, we can see what proportion of seasonal migration is captured in the clean scans.

```{r message=FALSE}
vp_mtr_cum50_cl %>%
  filter(status == "Accepted") %>%
  group_by(year, season, odim_code, day_night, momenttype) %>%
  summarise(total_prop = sum(prop)) %>%
  mutate(
    season_date = case_when(
      season == "spring" ~ as.Date(paste(year, "03-15", sep = "-")),
      season == "autumn" ~ as.Date(paste(year, "09-15", sep = "-")),
      TRUE ~ NA_Date_
    ),
    radar_nice = case_when(
      odim_code == "nlhrw" ~ "Herwijnen",
      odim_code == "nldhl" ~ "Den Helder"
    ),
    day_night = case_when(
      day_night == "daylight" ~ "day",
      day_night == "night" ~ "night",
    ),
    day_night_nice = case_when(
      day_night == "day" ~ "Day",
      day_night == "night" ~ "Night"
    )
  ) %>%
  ungroup() %>%
  identity() -> sp

sp %>%
  group_by(odim_code, radar_nice, momenttype) %>%
  summarise(
    mean_prop = mean(total_prop),
    min_prop = min(total_prop),
    max_prop = max(total_prop)
  ) %>%
  arrange(momenttype) %>%
  ungroup() -> sp_summary

sp_summary

sp %>%
  group_by(season, momenttype) %>%
  skim(total_prop) %>%
  arrange(momenttype)

unique_moments <- vp_mtr_cum50_cl %>% filter(momenttype == "2h30m", status == "Accepted") %>% count()
print(unique_moments)
```

```{r}
# Define the moon and sun symbols using Unicode
sp %>%
  mutate(total_prop = total_prop * 100) %>%
  ggplot() +
  geom_point(aes(x = season_date, y = total_prop, color = total_prop)) +
  geom_hline(data = sp_summary, aes(yintercept = mean_prop * 100), linetype = "dashed", color = "black") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  facet_wrap(vars(radar_nice, momenttype)) +
  xlab("Season") +
  ylab("% of migration mapped") +
  labs(title = "Seasonal proportion of migration included in map", color = "% of migration")

ggsave("data/plots/seasonal_props.pdf", width = 10, height = 6)
```

## Process scans to season-year stacks
With all RBCs processed and all clean migration moments gathered, we can create stacks of season-year combinations (e.g. autumn 2017, autumn 2018, spring 2019, spring 2021). We store all the individual RBCs' VIR parameters as individual layers and average them to a layer called `VIR` (and some transformations like `VIR_sqrt` and `VIR_log10`. While creating the stacks, we filter out areas where the RBC matches the following conditions:

1. `VIR` is above `2500`
2. `VIR` is exactly `0` (the pixel has never reflected)
3. There is rain in one of the elevation scans above the pixel
4. The adjustment factor `R` is above `10`.

```{r}
stack_rbcs <- function(rbcs, year_season, odimcode, daytime = "night", threshold_max = 2500, mean_method = "scans",
                       R_threshold = NULL, overwrite = FALSE, clutter_map = FALSE, momenttype) { # Added momenttype
  # See if files exist already
  if (is.null(R_threshold)) {
    R_text <- "null"
  } else {
    R_text <- R_threshold
  }

  basepath <- "data/stacks/"
  if (clutter_map) {
    basepath <- "data/stacks_clutter/"
  }

  filepath <- paste0(
    basepath,
    str_to_upper(odimcode), "_", year_season, "_thresh_", threshold_max, "_avg_", mean_method, "_", daytime, "_", R_text, "_", momenttype, ".RDS"
  )
  rasterpath <- paste0(
    basepath,
    str_to_upper(odimcode), "_", year_season, "_thresh_", threshold_max, "_avg_", mean_method, "_", daytime, "_", R_text, "_", momenttype, ".tif"
  )

  if (file.exists(filepath) && file.exists(rasterpath)) {
    if (!overwrite) {
      return("exists")
    }
  }

  r <- rbcs[[1]]
  rp <- r

  VIRs <- list()
  CLUTs <- list()

  for (i in seq_along(rbcs)) {
    VIR <- rbcs[[i]]$data@data$VIR
    CLUT <- rbcs[[i]]$data@data$VIR * 0
    R <- rbcs[[i]]$data@data$R
    RAIN <- rbcs[[i]]$data@data$rain
    # if (!clutter_map) {
    clutlocs <- which(VIR > threshold_max)
    VIR[clutlocs] <- NA
    CLUT[clutlocs] <- CLUT[clutlocs] + 1
    # } else {
    #   VIR[which(VIR > threshold_max)] <- threshold_max
    # }
    VIR[which(VIR == 0)] <- NA
    rainlocs <- which(RAIN > 0)
    # VIR[rainlocs] <- NA
    # CLUT[rainlocs] <- CLUT[rainlocs] + 1
    if (!is.null(R_threshold) && !clutter_map) {
      r_thresh_locs <- which(R_threshold > 10)
      VIR[r_thresh_locs] <- NA
      CLUT[r_thresh_locs] <- CLUT[r_thresh_locs] + 1
    }
    VIRs <- append(VIRs, list(VIR))
    CLUTs <- append(CLUTs, list(CLUT))
  }

  mVIR <- do.call(rbind, VIRs)
  mVIR[is.na(mVIR)] <- 0
  VIR_summed <- mVIR[1, ] * 0

  mCLUT <- do.call(rbind, CLUTs)
  CLUT_summed <- colSums(mCLUT)

  for (j in seq_along(VIRs)) {
    if (j == 1) {
      VIR_summed <- as.vector(as.matrix(mVIR[1:j, ]))
      rp$data@data[paste0("VIR_", j)] <- VIR_summed
      next
    }

    VIR_summed <- colSums(as.matrix(mVIR[1:j, ])) / j
    rp$data@data[paste0("VIR_", j)] <- as.numeric(VIR_summed)
  }

  remove_variables <- c("VID", "R", "overlap", "eta_sum", "eta_sum_expected", "rain")
  for (var in remove_variables) {
    rp$data@data[var] <- NULL
  }
  rp$data$VIR <- as.vector(as.matrix(rp$data@data[paste0("VIR_", length(VIRs))]))
  rp$data$CLUT <- as.numeric(CLUT_summed)

  rp <- calculate_param(rp, VIR_log10 = log10(VIR), VIR_log = log(VIR), VIR_sqrt = sqrt(VIR))
  saveRDS(rp, filepath)
  rrast <- terra::rast(rp$data)
  fixedlayers <- c("VIR", "VIR_log10", "VIR_log", "VIR_sqrt")
  layernames <- names(rrast)
  layerorder <- c(which(layernames %in% fixedlayers), which(!layernames %in% fixedlayers))
  rrast <- subset(rrast, layerorder)
  rf <- terra::writeRaster(rrast, rasterpath, overwrite = overwrite)
  return(filepath)
}

g <- expand.grid(
  year_season = unique(vp_mtr_cum50_cl$year_season),
  day_night = unique(vp_mtr_cum50_cl$day_night),
  odim_code = unique(vp_mtr_cum50_cl$odim_code),
  momenttype = unique(vp_mtr_cum50_cl$momenttype),
  stringsAsFactors = FALSE
)

generate_stacks <- function(year_season, day_night, odim_code, momenttype,
                             th = 2500,
                             R_threshold = 10,
                             overwrite = FALSE) {
  vp_mtr_cum50_cl %>%
    filter(status == "Accepted", year_season == !!year_season, day_night == !!day_night, odim_code == !!odim_code, momenttype == !!momenttype) %>%
    drop_na() %>%
    arrange(top) %>%
    dplyr::select(rbcfile, prop) -> files

  if (nrow(files) == 0) {
    return("files do not exist")
  }

  gr <- expand.grid(th = th, R_threshold = R_threshold, stringsAsFactors = FALSE)
  gr <- asplit(gr, 1)

  rbcs <- lapply(files$rbcfile, readRDS)
  lapply(gr, function(x) {
    stack_rbcs(
      rbcs = rbcs, year_season = year_season, odimcode = odim_code,
      threshold_max = as.numeric(x["th"]), R_threshold = as.numeric(x["R_threshold"]), overwrite = overwrite,
      momenttype = momenttype
    )
  })
}

processing_stacking <- pbmcmapply(generate_stacks,
  year_season = g$year_season, day_night = g$day_night, odim_code = g$odim_code, momenttype = g$momenttype,
  overwrite = TRUE, mc.cores = 6, mc.preschedule = FALSE
)
saveRDS(processing_stacking, paste0("data/logs/processing_stacking_", format(Sys.time(), "%Y%m%dT%H%M"), ".RDS"))
```

## Combine season stacks to radar, period stacks
Now we can continue simply creating averages of the season-year stacks, resulting in rasters of average `VIR` per season per radar. We also limit the domain of the stacks to 100km from the radar now.

```{r}
final_stacks <- expand.grid(
  odim_code = c("NLHRW", "NLDHL"),
  season = c("spring", "autumn"),
  daytime = c("night"),
  th = 2500,
  mm = c("scans"),
  R_threshold = 10,
  momenttype = unique(vp_mtr_cum50_cl$momenttype),
  stringsAsFactors = FALSE
)

for (i in 1:nrow(final_stacks)) {
  fs <- final_stacks[i, ]

  rastfiles <- Sys.glob(
    paste0("data/stacks/", str_to_upper(fs$odim_code), "_*_", fs$season, "_thresh_", fs$th, "_avg_", fs$mm, "_", fs$daytime, "_", fs$R_threshold, "_", fs$momenttype, ".tif")
  )

  stk <- terra::rast(lapply(rastfiles, function(x) {
    tryCatch(terra::rast(x, lyrs = "VIR"),
             error = function(err) {
               print(err)
             }
    )
  }))
  rmean <- app(stk, mean)
  names(rmean) <- "vir_mean"

  stk <- terra::rast(lapply(rastfiles, function(x) {
    tryCatch(terra::rast(x, lyrs = "CLUT"),
             error = function(err) {
               print(err)
             }
    )
  }))
  csum <- app(stk, sum)
  csum <- csum / minmax(csum)[2]
  names(csum) <- "clut_sum"

  file_out <- paste0(
    "data/final_stacks/", fs$daytime, "/", fs$mm, "/",
    fs$odim_code, "_", fs$season, "_thresh_", fs$th, "_avg_", fs$mm, "_", fs$daytime, "_", fs$R_threshold, "_", fs$momenttype, ".tif"
  )
  if (!dir.exists(dirname(file_out))) dir.create(dirname(file_out), recursive = TRUE)

  if (fs$odim_code == "NLHRW") {
    lat <- 51.8371
    lon <- 5.138
  }
  if (fs$odim_code == "NLDHL") {
    lat <- 52.9528
    lon <- 4.79061
  }

  circle_radius <- 100000 # 100 km in meters

  # Create a simple features (sf) point object
  center_point <- st_sfc(st_point(c(lon, lat)))

  # Buffer the point to create a circular polygon
  st_crs(center_point) <- 4326
  center_point <- st_transform(center_point, crs = st_crs(rmean))
  circle <- st_buffer(center_point, dist = circle_radius)
  masked_raster <- st_rasterize(st_as_sf(circle), st_as_stars(st_bbox(rmean, values = NA_real_), nx = 640, ny = 640))
  masked_raster[masked_raster == 0] <- NA

  raster_masked <- terra::mask(rmean, as(masked_raster, "SpatRaster"))
  clut_masked <- terra::mask(csum, as(masked_raster, "SpatRaster"))

  writeRaster(raster_masked, file_out, overwrite = TRUE)
  writeRaster(clut_masked, paste0(tools::file_path_sans_ext(file_out), "_clut.tif"), overwrite = TRUE)
}
```

## Uncertainty analysis of spatial patterns using leave-one-out jack-knife

```{r}
final_stacks <- expand.grid(
  odim_code = c("NLHRW", "NLDHL"),
  season = c("spring", "autumn"),
  daytime = c("night"),
  th = 2500,
  mm = c("scans"),
  R_threshold = 10,
  momenttype = unique(vp_mtr_cum50_cl$momenttype),
  stringsAsFactors = FALSE
)

overall_correlations <- list()

for (i in 1:nrow(final_stacks)) {
  fs <- final_stacks[i, ]

  rastfiles <- Sys.glob(
    paste0("data/stacks/", str_to_upper(fs$odim_code), "_*_", fs$season, "_thresh_", fs$th, "_avg_", fs$mm, "_", fs$daytime, "_", fs$R_threshold, "_", fs$momenttype, ".tif")
  )

  stk <- terra::rast(lapply(rastfiles, function(x) {
    tryCatch(terra::rast(x, lyrs = "VIR"),
             error = function(err) {
               print(err)
             }
    )
  }))
  if (fs$odim_code == "NLHRW") {
    lat <- 51.8371
    lon <- 5.138
  }
  if (fs$odim_code == "NLDHL") {
    lat <- 52.9528
    lon <- 4.79061
  }

  circle_radius <- 100000 # 100 km in meters

  # Create a simple features (sf) point object
  center_point <- st_sfc(st_point(c(lon, lat)))

  # Buffer the point to create a circular polygon
  st_crs(center_point) <- 4326
  center_point <- st_transform(center_point, crs = st_crs(stk))
  circle <- st_buffer(center_point, dist = circle_radius)
  masked_raster <- st_rasterize(st_as_sf(circle), st_as_stars(st_bbox(stk, values = NA_real_), nx = 640, ny = 640))
  masked_raster[masked_raster == 0] <- NA
  
  stk_masked <- terra::mask(stk, as(masked_raster, "SpatRaster"))
  stk_full_mean <- mean(stk_masked)
  
  correlations <- numeric(nlyr(stk_masked))
  
  for (j in 1:nlyr(stk_masked)) {
    stk_subset <- stk_masked[[-j]]
    stk_mean_subset <- mean(stk_subset)
    
    correlations[j] <- cor(values(stk_mean_subset, na.rm = TRUE), 
                           values(stk_full_mean, na.rm = TRUE), use = "complete.obs")
  }
  
  names(correlations) <- 2017:2022
  
  overall_correlations[[i]] <- list(
    radar = fs$odim_code,
    season = fs$season,
    momenttype = fs$momenttype,
    correlations = correlations
  )
}

cor_df <- do.call(rbind, lapply(overall_correlations, function(entry) {
  data.frame(
    radar = entry$radar,
    season = entry$season,
    momenttype = entry$momenttype,
    correlation = entry$correlations,
    year_left_out = names(entry$correlations)
  )
}))
rownames(cor_df) <- NULL
cor_df %>%
  group_by(radar, season, momenttype) %>%
  skim(correlation)
```

## Uncertainty analysis of spatial patterns 2h30m vs. 4h00m

```{r}
final_stacks <- expand.grid(
  odim_code = c("NLHRW", "NLDHL"),
  season = c("spring", "autumn"),
  daytime = c("night"),
  th = 2500,
  mm = c("scans"),
  R_threshold = 10,
  stringsAsFactors = FALSE
)

overall_correlations <- list()

for (i in 1:nrow(final_stacks)) {
  fs <- final_stacks[i, ]

  rastfiles_2h30 <- Sys.glob(
    paste0("data/stacks/", str_to_upper(fs$odim_code), "_*_", fs$season, "_thresh_", fs$th, "_avg_", fs$mm, "_", fs$daytime, "_", fs$R_threshold, "_", "2h30m", ".tif")
  )
  
  rastfiles_4h00 <- Sys.glob(
    paste0("data/stacks/", str_to_upper(fs$odim_code), "_*_", fs$season, "_thresh_", fs$th, "_avg_", fs$mm, "_", fs$daytime, "_", fs$R_threshold, "_", "4h00m", ".tif")
  )

  stk_2h30 <- terra::rast(lapply(rastfiles_2h30, function(x) {
    tryCatch(terra::rast(x, lyrs = "VIR"),
             error = function(err) {
               print(err)
             }
    )
  }))
  
  stk_4h00 <- terra::rast(lapply(rastfiles_4h00, function(x) {
    tryCatch(terra::rast(x, lyrs = "VIR"),
             error = function(err) {
               print(err)
             }
    )
  }))
  if (fs$odim_code == "NLHRW") {
    lat <- 51.8371
    lon <- 5.138
  }
  if (fs$odim_code == "NLDHL") {
    lat <- 52.9528
    lon <- 4.79061
  }

  circle_radius <- 100000 # 100 km in meters

  # Create a simple features (sf) point object
  center_point <- st_sfc(st_point(c(lon, lat)))

  # Buffer the point to create a circular polygon
  st_crs(center_point) <- 4326
  center_point <- st_transform(center_point, crs = st_crs(stk_2h30))
  circle <- st_buffer(center_point, dist = circle_radius)
  masked_raster <- st_rasterize(st_as_sf(circle), st_as_stars(st_bbox(stk_2h30, values = NA_real_), nx = 640, ny = 640))
  masked_raster[masked_raster == 0] <- NA
  
  stk_masked_2h30 <- terra::mask(stk_2h30, as(masked_raster, "SpatRaster"))
  stk_masked_4h00 <- terra::mask(stk_4h00, as(masked_raster, "SpatRaster"))

  correlations <- numeric(nlyr(stk_masked_2h30))
  
  for (j in 1:nlyr(stk_masked_2h30)) {
    stk_subset_2h30 <- stk_masked_2h30[[-j]]
    stk_subset_4h00 <- stk_masked_4h00[[-j]]
    stk_mean_subset_2h30 <- mean(stk_subset_2h30)
    stk_mean_subset_4h00 <- mean(stk_subset_4h00)
    
    correlations[j] <- cor(values(stk_mean_subset_2h30, na.rm = TRUE), 
                           values(stk_mean_subset_4h00, na.rm = TRUE), use = "complete.obs")
  }
  
  names(correlations) <- 2017:2022
  
  overall_correlations[[i]] <- list(
    radar = fs$odim_code,
    season = fs$season,
    correlations = correlations
  )
}

cor_df_momenttype <- do.call(rbind, lapply(overall_correlations, function(entry) {
  data.frame(
    radar = entry$radar,
    season = entry$season,
    correlation = entry$correlations,
    year_left_out = names(entry$correlations)
  )
}))
rownames(cor_df_momenttype) <- NULL
cor_df_momenttype %>%
  group_by(radar, season) %>%
  skim(correlation) %>%
  dplyr::select(-c(n_missing, complete_rate, skim_variable))
```


## Combine radar, time stacks to national-level maps

We can now combine the radar-level seasonal averages to national-level maps per season. In the overlap zone between both radars, we use max-compositing as this provides the smoothest transition in average `VIR` values between the radars.

```{r}
final_stacks <- expand.grid(
  season = c("spring", "autumn"),
  daytime = c("night"),
  th = c(2500),
  mm = c("scans"),
  zmax = c(750),
  R_threshold = 10,
  momenttype = unique(vp_mtr_cum50_cl$momenttype),
  stringsAsFactors = FALSE
)

fstacks <- asplit(final_stacks, 1)

save_map <- function(x, overwrite = FALSE, cluttermap = FALSE, mode = "dark") {
  fs <- x

  basepath_stacks <- "data/final_stacks/"
  if (cluttermap) basepath_stacks <- "data/final_stacks_clutter/"
  basepath_maps <- "data/maps/"
  if (cluttermap) basepath_maps <- "data/maps_clutter/"
  basepath_plots <- "data/maps_plots/VIR_"
  if (cluttermap) basepath_plots <- "data/maps_plots_clutter/VIR_"

  fstacks <- paste0(
    basepath_stacks, fs["daytime"], "/", fs["mm"], "/", c("NLHRW", "NLDHL"), "_",
    fs["season"], "_thresh_", fs["th"], "_avg_", fs["mm"], "_", fs["daytime"], "_", fs["R_threshold"], "_", fs["momenttype"], ".tif"
  )
  fstacks <- str_replace_all(fstacks, " ", "")
  clutstacks <- paste0(tools::file_path_sans_ext(fstacks), "_clut.tif")
  clutstacks <- str_replace_all(clutstacks, " ", "")
  mapfile <- paste0(
    basepath_maps, fs["daytime"], "/", fs["mm"],
    "/NL_", fs["season"], "_", fs["daytime"], "_thresh_", fs["th"], "_avg_", fs["mm"], "_", fs["R_threshold"], "_", fs["momenttype"], ".tif"
  )
  mapfile <- str_replace_all(mapfile, " ", "")

  if (file.exists(mapfile) & !overwrite) {
    return(mapfile)
  }

  if (!dir.exists(dirname(mapfile))) dir.create(dirname(mapfile), recursive = TRUE)

  mapfile_plot <- paste0(
    basepath_plots, fs["zmax"], "/", fs["daytime"], "/", fs["mm"], "/NL_",
    fs["season"], "_", fs["daytime"], "_thresh_", fs["th"], "_avg_", fs["mm"], "_", fs["R_threshold"], "_", fs["momenttype"], ".png"
  )
  mapfile_plot <- str_replace_all(mapfile_plot, " ", "")
  if (!dir.exists(dirname(mapfile_plot))) dir.create(dirname(mapfile_plot), recursive = TRUE)

  r1 <- rast(fstacks[1]) %>% project("EPSG:28992")
  r2 <- rast(fstacks[2]) %>% project("EPSG:28992")

  bbox1 <- ext(r1)
  bbox2 <- ext(r2)

  combined_bbox <- c(min(bbox1$xmin, bbox2$xmin), max(bbox1$xmax, bbox2$xmax), min(bbox1$ymin, bbox2$ymin), max(bbox1$ymax, bbox2$ymax))

  rn <- rast(ext = combined_bbox, crs = "EPSG:28992")
  res(rn) <- 500

  r1_resampled <- resample(r1, rn)
  r2_resampled <- resample(r2, rn)

  m <- mosaic(sprc(r1_resampled, r2_resampled), fun = max)
  writeRaster(m, mapfile, overwrite = TRUE)

  r1_clut <- rast(clutstacks[1]) %>% project("EPSG:28992")
  r2_clut <- rast(clutstacks[2]) %>% project("EPSG:28992")

  r1_resampled_clut <- resample(r1_clut, rn)
  r2_resampled_clut <- resample(r2_clut, rn)

  m_clut <- mosaic(sprc(r1_resampled_clut, r2_resampled_clut), fun = max)
  writeRaster(m_clut, paste0(tools::file_path_sans_ext(mapfile), "_clut.tif"), overwrite = TRUE)

  maps <- c(m, m_clut)

  data <- raster::as.data.frame(maps, xy = TRUE)

  c <- crs(m)
  nl <- geojsonsf::geojson_sfc("data/gis/Netherlands.geojson") %>% st_transform(c)
  nhol <- geojsonsf::geojson_sfc("data/gis/Noord-Holland.geojson") %>% st_transform(c)
  nhol_buf <- geojsonsf::geojson_sfc("data/gis/Noord-Holland-10km-Buffer.geojson") %>% st_transform(c)
  radar_buf <- geojsonsf::geojson_sf("data/gis/Radars-100km-Buffer.geojson") %>% st_transform(c)

  radar_bbox <- st_bbox(radar_buf)

  padding <- 500
  xlim <- c(radar_bbox$xmin - padding, radar_bbox$xmax + padding)
  ylim <- c(radar_bbox$ymin - padding, radar_bbox$ymax + padding)
  zlim <- c(0, as.numeric(fs["zmax"]))
  tod <- if_else(fs["daytime"] == "night", "by Night", "by Day")
  title <- paste0(str_to_sentence(fs["season"]), " ", tod)

  if (mode == "dark") {
    ggplot(data) +
      geom_raster(aes(x = x, y = y, fill = vir_mean / 11)) +
      scale_fill_viridis_c(limits = zlim / 11, name = "Mean\nVID", oob = scales::squish, option = "inferno") +
      geom_sf(data = nl, fill = "NA", color = "white", linewidth = .3) +
      geom_sf(data = radar_buf, fill = "NA", color = "#ffffffaa", linewidth = .3) +
      coord_sf(xlim = xlim, ylim = ylim, expand = FALSE) +
      ggtitle(title) +
      dark_theme_minimal() +
      theme(
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(size = 14),
        plot.subtitle = element_text(size = 10),
        axis.text = element_text(color = alpha("white", 0.25)),
        panel.grid.major = element_line(color = alpha("white", 0.1)),
        panel.grid.minor = element_line(color = "white"),
        plot.title.position = "plot",
        legend.position = c(1.02, 0.66),
        plot.margin = unit(c(1, 1, 1, 1), "cm")
      ) -> pl1
  } else if (mode == "light") {
    ggplot(data) +
      geom_raster(aes(x = x, y = y, fill = vir_mean / 11)) +
      scale_fill_viridis_c(limits = zlim / 11, name = "Mean\nVID", oob = scales::squish, option = "inferno") +
      geom_sf(data = nl, fill = "NA", color = "black", linewidth = .3) +
      geom_sf(data = radar_buf, fill = "NA", color = "#000000aa", linewidth = .3) +
      coord_sf(xlim = xlim, ylim = ylim, expand = FALSE) +
      ggtitle(title) +
      theme(
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(size = 14),
        plot.subtitle = element_text(size = 10),
        axis.text = element_text(color = alpha("black", 0.25)),
        panel.grid.major = element_line(color = alpha("black", 0.1)),
        panel.grid.minor = element_line(color = "black"),
        plot.title.position = "plot",
        legend.position = c(1.02, 0.66),
        legend.background = element_rect(fill = "#00000000"),
        plot.margin = unit(c(1, 1, 1, 1), "cm")
      ) -> pl1
  }

  ggsave(mapfile_plot, plot = pl1, width = 5, height = 6)
}

processing <- pbmclapply(fstacks, save_map, overwrite = TRUE, mode = "light", mc.cores = 10, mc.preschedule = FALSE)

saveRDS(processing, paste0("data/logs/processing_mapping_", format(Sys.time(), "%Y%m%dT%H%M"), ".RDS"))
```

# Clutter map creation
Now for the clutter map creation, we follow exactly the same approach up to now, but rather than looking at the migration peaks, we select the scans which supposedly have the least migration.

We start with selecting the lowest 25 scans in terms of nightly migration for each season.

```{r}
vp_mtr %>%
  group_by(year_season, odim_code, day_night) %>%
  filter(top >= tail(top, 25)[1]) %>% 
  identity() -> vp_mtr_low

scantimes <- as_datetime(unlist(apply(vp_mtr_low, MARGIN = 1, FUN = calculate_scantime, simplify = FALSE)))

vp_mtr_low$moment <- scantimes
vp_mtr_low
```
We download the corresponding polar volume files.

```{r}
dts <- dplyr::select(vp_mtr_low, odim_code, moment)

dts_hrw <- dts %>%
  filter(odim_code == "nlhrw") %>%
  pull(moment)

filepaths_hrw <- paste0(
  "minio/pvol/NL/HRW/", year(dts_hrw), "/", sprintf("%02d", month(dts_hrw)), "/", sprintf("%02d", day(dts_hrw)), "/",
  "NLHRW_pvol_", format(dts_hrw, format = "%Y%m%dT%H%M"), "_6356.h5"
)
filepaths_hrw_alt <- paste0(
  "minio/pvol/NL/HRW/", year(dts_hrw), "/", sprintf("%02d", month(dts_hrw)), "/", sprintf("%02d", day(dts_hrw)), "/",
  "NLHRW_pvol_", format(dts_hrw, format = "%Y%m%dT%H%M"), "_NL52.h5"
)
paths <- list(paste0("mc cp ", filepaths_hrw, " ."), paste0("mc cp ", filepaths_hrw_alt, " ."))

write_lines(unlist(paths), file = "data/pvol_clutter/hrw_files.sh", )

dts_dhl <- dts %>%
  filter(odim_code == "nldhl") %>%
  pull(moment)

filepaths_dhl <- paste0(
  "minio/pvol/NL/DHL/", year(dts_dhl), "/", sprintf("%02d", month(dts_dhl)), "/", sprintf("%02d", day(dts_dhl)), "/",
  "NLDHL_pvol_", format(dts_dhl, format = "%Y%m%dT%H%M"), "_6234.h5"
)
filepaths_dhl_alt <- paste0(
  "minio/pvol/NL/DHL/", year(dts_dhl), "/", sprintf("%02d", month(dts_dhl)), "/", sprintf("%02d", day(dts_dhl)), "/",
  "NLDHL_pvol_", format(dts_dhl, format = "%Y%m%dT%H%M"), "_NL51.h5"
)
paths <- list(paste0("mc cp ", filepaths_dhl, " ."), paste0("mc cp ", filepaths_dhl_alt, " ."))

write_lines(unlist(paths), file = "data/pvol_clutter/dhl_files.sh", )
```

And we process the files following the procedure in `rbc_preprocessing.R`. Afterwards, we screen scans again to remove cases with rain, anomalous propagation. We save information on the screening outcomes, to gather files to continue working with.

```{r}
accepted_files <- list.files("data/rbc_png_clutter/full/Accepted/")
rejected_files <- list.files("data/rbc_png_clutter/full/Rejected/")

rbc_file_from_png <- function(file, azim_method = "full") {
  f <- basename(file)
  ss <- str_split(f, "_")[[1]][1:4]
  radar <- str_to_lower(ss[1])
  moment <- parse_date_time(ss[3], "YmdHM")
  fp <- paste0("data/rbc_clutter/", str_c(ss, collapse = "_"), "_", azim_method, ".RDS")
  return(list("odim_code" = radar, "moment" = moment, "rbcfile" = fp))
}

accepted <- bind_rows(lapply(accepted_files, rbc_file_from_png)) %>% mutate(status = "Accepted")
rejected <- bind_rows(lapply(rejected_files, rbc_file_from_png)) %>% mutate(status = "Rejected")

classified_moments <- bind_rows(accepted, rejected)

vp_mtr_low %>%
  left_join(classified_moments, by = join_by(odim_code, moment)) %>%
  mutate(status = replace_na(status, "Rejected")) %>%
  identity() -> vp_mtr_low_cl
```

And again we can make the season-year stacks.

```{r}
g <- expand.grid(year_season = unique(vp_mtr_low_cl$year_season),
                 day_night = unique(vp_mtr_low_cl$day_night),
                 odim_code = unique(vp_mtr_low_cl$odim_code))

generate_stacks <- function(year_season, day_night, odim_code,
                            th = 2500,
                            R_threshold = 10,
                            overwrite = FALSE) {
  
  vp_mtr_low_cl %>%
    filter(status == "Accepted", year_season == !!year_season, day_night == !!day_night, odim_code == !!odim_code) %>%
    drop_na() %>%
    arrange(top) %>%
    dplyr::select(rbcfile, prop) -> files
  
  if (nrow(files) == 0) return("files do not exist")
  
  gr <- expand.grid(th = th, R_threshold = R_threshold, stringsAsFactors = FALSE)
  gr <- asplit(gr, 1)
  
  rbcs <- lapply(files$rbcfile, readRDS)
  lapply(gr, function(x) {stack_rbcs(rbcs = rbcs, year_season = year_season, odimcode = odim_code, 
                                     threshold_max = as.numeric(x["th"]), R_threshold = x["R_threshold"], overwrite = overwrite, clutter_map = TRUE)})
}

processing_stacking <- pbmcmapply(generate_stacks, year_season = g$year_season, day_night = g$day_night, 
                                odim_code = g$odim_code, overwrite = TRUE, mc.cores = 6, mc.preschedule = TRUE)
saveRDS(processing_stacking, paste0("data/logs/processing_stacking_clutter_", format(Sys.time(), "%Y%m%dT%H%M"), ".RDS"))
```

Which now we'll aggregate to to seasonal averages.

```{r}
final_stacks <- expand.grid(
  odim_code = c("NLHRW", "NLDHL"),
  season = c("spring", "autumn"),
  daytime = c("night"),
  th = 2500,
  mm = c("scans"),
  R_threshold = 10
)

for (i in 1:nrow(final_stacks)) {
  fs <- final_stacks[i, ]
  
  rastfiles <- Sys.glob(
    paste0("data/stacks_clutter/", str_to_upper(fs$odim_code), "_*_", fs$season, "_thresh_", fs$th, "_avg_", 
           fs$mm, "_", fs$daytime, "_", fs$R_threshold, ".tif")
  )
  
  stk <- terra::rast(lapply(rastfiles, function(x) {
    tryCatch(terra::rast(x, lyrs = "VIR"), 
             error = function(err) {
               print(err)
             })
  }))
  
  rmean <- app(stk, mean) 
  names(rmean) <- "vir_mean"
  
  stk <- terra::rast(lapply(rastfiles, function(x) {
    tryCatch(terra::rast(x, lyrs = "CLUT"),
      error = function(err) {
        print(err)
      }
    )
  }))
  csum <- app(stk, sum)
  csum <- csum / minmax(csum)[2]
  names(csum) <- "clut_sum"
  
  file_out <- paste0("data/final_stacks_clutter/", fs$daytime, "/", fs$mm, "/", 
                     fs$odim_code, "_", fs$season, "_thresh_", fs$th, "_avg_", fs$mm, "_", fs$daytime, "_", fs$R_threshold, ".tif")
  if (!dir.exists(dirname(file_out))) dir.create(dirname(file_out), recursive = TRUE)
  
  if (fs$odim_code == "NLHRW") {
    lat <- 51.8371
    lon <- 5.138
  }
  if (fs$odim_code == "NLDHL") {
    lat <- 52.9528
    lon <- 4.79061
  }
  
  circle_radius <- 100000  # 100 km in meters

  # Create a simple features (sf) point object
  center_point <- st_sfc(st_point(c(lon, lat)))
  
  # Buffer the point to create a circular polygon
  st_crs(center_point) <- 4326
  center_point <- st_transform(center_point, crs = st_crs(rmean))
  circle <- st_buffer(center_point, dist = circle_radius)
  masked_raster <- st_rasterize(st_as_sf(circle), st_as_stars(st_bbox(rmean, values = NA_real_), nx = 640, ny = 640))
  masked_raster[masked_raster == 0] <- NA
  
  raster_masked <- terra::mask(rmean, as(masked_raster, "SpatRaster"))
  clut_masked <- terra::mask(csum, as(masked_raster, "SpatRaster"))
  
  writeRaster(raster_masked, file_out, overwrite = TRUE)
  writeRaster(clut_masked, paste0(tools::file_path_sans_ext(file_out), "_clut.tif"), overwrite = TRUE)
}
```

And now we convert it into a national-level map of clutter contamination again.

```{r}
final_stacks <- expand.grid(season = c("spring", "autumn"),
                            daytime = c("night"),
                            th = c(2500),
                            mm = c("scans"),
                            zmax = c(2000),
                            R_threshold = 10)

fstacks <- asplit(final_stacks, 1)
processing <- lapply(fstacks, save_map, cluttermap = TRUE, overwrite = TRUE)

saveRDS(processing, paste0("data/logs/processing_mapping_", format(Sys.time(), "%Y%m%dT%H%M"), ".RDS"))
```

# Clutter removal

```{r}
clutter_maps <- expand.grid(season = c("spring", "autumn"),
                            daytime = c("night"),
                            # thresh = c(25, 50, 100, 150, 200, 250, 300),
                            thresh = c(250),
                            # s = c(1, 2, 3, 4, 5, 6, 7),
                            # n = c(13, 17, 21, 25, 29),
                            s = c(4),
                            n = c(25),
                            momenttype = unique(vp_mtr_cum50_cl$momenttype),
                            stringsAsFactors = FALSE)
# clutter_maps <- expand.grid(season = c("spring", "autumn"),
#                             daytime = c("night"),
#                             thresh = c(250),
#                             s = c(4),
#                             n = c(25),
#                             stringsAsFactors = FALSE)

create_final_map_set <- function(map_grid, buffer_patches = NULL,
                                 custom_clutter = NULL) {
  cm <- asplit(map_grid, 1)

  for (m in cm) {
    t <- as.numeric(m["thresh"])
    r <- rast(paste0("data/maps/", m["daytime"], "/scans/NL_", m["season"], "_", m["daytime"],
                     "_thresh_2500_avg_scans_10_", m["momenttype"], ".tif"))
    if (is.null(custom_clutter)) {
      rc <- rast(paste0("data/maps_clutter/", m["daytime"], "/scans/NL_", m["season"], "_", m["daytime"],
                        "_thresh_2500_avg_scans_10.tif"))
      rc2 <- rast(paste0("data/maps/", m["daytime"], "/scans/NL_", m["season"], "_", m["daytime"],
                        "_thresh_2500_avg_scans_10_", m["momenttype"], "_clut.tif"))
      print(rc2)
      # Create denoised clutter map
      rc[rc < t] <- NA
      rc[rc >= t] <- 1
      rc2[rc2 > 0.25] <- 1
      rc2[rc2 != 1] <- NA
      rc <- rc | rc2
    } else {
      if (is.logical(custom_clutter)) {
        rc <- rast(paste0("data/final_maps/custom_clutter/NL_", m["season"], "_", m["daytime"], ".tif"))
      } else if (is.character(custom_clutter)) {
        rc <- rast(custom_clutter)
      }
    }
    
    s <- as.numeric(m["s"])
    n <- as.numeric(m["n"])
    
    # Prepare GIS data for plots
    c <- crs(r)
    nl <- geojsonsf::geojson_sfc("data/gis/Netherlands.geojson") %>% st_transform(c)
    nhol <- geojsonsf::geojson_sfc("data/gis/Noord-Holland.geojson") %>% st_transform(c)
    nhol_buf <- geojsonsf::geojson_sfc("data/gis/Noord-Holland-10km-Buffer.geojson") %>% st_transform(c)
    radar_buf <- geojsonsf::geojson_sf("data/gis/Radars-100km-Buffer.geojson") %>% st_transform(c)
    
    prc <- patches(rc)
    zrc <- zonal(cellSize(prc, unit = "km"), prc, sum, as.raster = TRUE)
    src <- ifel(zrc < 0.5, NA, prc)
    rcn <- rc
    rcn[is.na(src)] <-NA
    
    if (!is.null(buffer_patches)) {
      rcn <- buffer(rcn, width = buffer_patches)
      rcn <- rcn * 1
      rcn[rcn == 0] <- NA
    }
    
    cluts <- c(rc, rcn)
    cls <- as.data.frame(cluts, xy = TRUE)
    colnames(cls) <- c("x", "y", "clut_orig", "clut_denoised")
    cls %>% pivot_longer(cols = -c(x, y), names_to = "clut_type") %>% drop_na() -> cls
    ggplot() +
      geom_raster(aes(x = x, y = y, fill = clut_type, group = clut_type), data = cls) +
      facet_wrap(~clut_type) +
      dark_theme_minimal() +
      geom_sf(data = nl, fill = "NA", color = "white", linewidth = .3) +
      geom_sf(data = nhol, fill = "NA", color = "white", linewidth = .3) +
      geom_sf(data = radar_buf, fill = "NA", color = "white", linewidth = .3) +
      theme(axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            plot.title = element_text(size = 14),
            plot.subtitle = element_text(size = 10),
            axis.text = element_text(color = alpha("white", 0.25)),
            panel.grid.major = element_line(color = alpha("white", 0.1)),
            panel.grid.minor = element_line(color = "white"),
            plot.title.position = "plot",
            plot.margin = unit(c(1,1,1,1), "cm")) -> pclut
    
    # Save plot
    fp_clutplot <- paste0("data/final_maps/NL_", m["season"], "_", m["daytime"], 
                          "_thresh_", t, "_s_", s, "_n_", n, "_", m["momenttype"], "_clut.png")
    ggsave(pclut, width = 7, height = 4, filename = fp_clutplot)
    
    # Save clutter map
    fp_clut <- paste0("data/final_maps/NL_", m["season"], "_", m["daytime"], 
                      "_thresh_", t, "_s_", s, "_n_", n, "_", m["momenttype"], "_clutter.tif")
    writeRaster(rcn, fp_clut, overwrite = TRUE)
    
    # Create final bird map
    rn <- r
    rn[rcn == 1] <- NA
    
    # Blur
    suppressMessages({
      b <- raster.gaussian.smooth(rn, s=s, n=n, na.rm = TRUE, type = "mean")
    })
    
    # Remove area introduced by blur
    b[is.na(r)] <- NA
    
    # Save bird map
    fp_bird <- paste0("data/final_maps/NL_", m["season"], "_", m["daytime"], 
                      "_thresh_", t, "_s_", s, "_n_", n, "_", m["momenttype"], ".tif")
    writeRaster(b, fp_bird, overwrite = TRUE)
    
    # Plots for quick overviews
    if (m["season"] == "autumn") {
      zlims <- c(0, 800)
    } else if (m["season"] == "spring") {
      zlims <- c(0, 800)
    }
    
    data <- as.data.frame(b, xy = TRUE)
    clut <- as.data.frame(rcn, xy = TRUE)
    
    ggplot() +
      geom_raster(aes(x = x, y = y, fill = focal_mean), data = data) +
      scale_fill_viridis_c(limits = zlims, oob = scales::squish, option = "inferno", na.value = 0, name = "Mean VIR") +
      new_scale_fill() +
      geom_raster(data = clut, aes(x = x, y = y), fill = alpha("black", 0.4)) +
      geom_sf(data = nl, fill = "NA", color = "white", linewidth = .3) +
      geom_sf(data = nhol, fill = "NA", color = "white", linewidth = .3) +
      geom_sf(data = radar_buf, fill = "NA", color = "white", linewidth = .3) +
      dark_theme_minimal() +
      labs(title = paste0(str_to_sentence(m["season"]), " by ", m["daytime"])) +
      theme(axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            plot.title = element_text(size = 14),
            plot.subtitle = element_text(size = 10),
            # axis.text.x = element_text(color = "white"),
            # axis.text.y = element_text(color = "white"),
            axis.text = element_text(color = alpha("white", 0.25)),
            panel.grid.major = element_line(color = alpha("white", 0.1)),
            panel.grid.minor = element_line(color = "white"),
            plot.title.position = "plot",
            plot.margin = unit(c(1,1,1,1), "cm"))-> p
    
    # Save plot
    fp_plot <- paste0("data/final_maps/NL_", m["season"], "_", m["daytime"], 
                      "_thresh_", t, "_s_", s, "_n_", n, "_", m["momenttype"], ".png")
    ggsave(p, filename = fp_plot)
    
    # Log
    print(m)
  }
}

create_final_map_set(clutter_maps, buffer_patches = 500)
```

After a visual inspection of the plots above created with a grid of settings (see commented out), we have settled on using clutter maps with a VIR threshold of 250.

# Beam blockage

After calculating beam blockage using "beam-blockage/beamblockage.ipynb", which can also be found in [the wradlib package documentation](https://docs.wradlib.org/en/1.19.1/notebooks/beamblockage/wradlib_beamblock.html), two .csv's storing x,y,z and CBB (cumulative beam blockage) values are created for both HRW and DHL radars. We will turn these in raster files which can be used in this project.

```{r}
hrw_bb <- read_csv("data/beam_blockage/hrw.csv", col_types = "dddddd") %>% 
  dplyr::select(x, y, CBB)

dhl_bb <- read_csv("data/beam_blockage/dhl.csv", col_types = "dddddd") %>%
  dplyr::select(x, y, CBB)

exrast_hrw <- rast("data/final_stacks/night/scans/NLHRW_autumn_thresh_2500_avg_scans_night_10_2h30m.tif")
exrast_dhl <- rast("data/final_stacks/night/scans/NLDHL_autumn_thresh_2500_avg_scans_night_10_2h30m.tif")

v_hrw <- vect(hrw_bb, geom = c("x", "y"), crs = "epsg:4326") %>% project(exrast_hrw)
v_dhl <- vect(dhl_bb, geom = c("x", "y"), crs = "epsg:4326") %>% project(exrast_dhl)

cbb_hrw <- rasterize(v_hrw, exrast_hrw, field = "CBB", fun = max) %>%
  focal(w = c(5, 5), fun = "max", na.rm = TRUE)
cbb_dhl <- rasterize(v_dhl, exrast_dhl, field = "CBB", fun = max) %>%
  focal(w = c(5, 5), fun = "max", na.rm = TRUE)
writeRaster(cbb_hrw, "data/beam_blockage/hrw.tif", overwrite = TRUE)
writeRaster(cbb_dhl, "data/beam_blockage/dhl.tif", overwrite = TRUE)

plot(cbb_hrw)
plot(cbb_dhl)

clip_to_radius <- function(raster_full, odim_code, radius) {
  if (odim_code == "NLHRW") {
    lat <- 51.8371
    lon <- 5.138
  }
  if (odim_code == "NLDHL") {
    lat <- 52.9528
    lon <- 4.79061
  }
  
  circle_radius <- radius  # 100 km in meters

  # Create a simple features (sf) point object
  center_point <- st_sfc(st_point(c(lon, lat)))
  
  # Buffer the point to create a circular polygon
  st_crs(center_point) <- 4326
  center_point <- st_transform(center_point, crs = st_crs(raster_full))
  circle <- st_buffer(center_point, dist = circle_radius)
  # mask(x = raster_data, mask = circle)  
  masked_raster <- st_rasterize(st_as_sf(circle), st_as_stars(st_bbox(raster_full, values = NA_real_), nx = 640, ny = 640))
  masked_raster[masked_raster == 0] <- NA
  
  raster_masked <- terra::mask(raster_full, as(masked_raster, "SpatRaster"))
  raster_masked
}

r1 <- cbb_hrw %>% clip_to_radius("NLHRW", 100000) %>% project("EPSG:28992")
r2 <- cbb_dhl %>% clip_to_radius("NLDHL", 100000) %>% project("EPSG:28992")

bbox1 <- ext(r1)
bbox2 <- ext(r2)

combined_bbox <- c(min(bbox1$xmin, bbox2$xmin), max(bbox1$xmax, bbox2$xmax), 
                   min(bbox1$ymin, bbox2$ymin), max(bbox1$ymax, bbox2$ymax))

rn <- rast(ext = combined_bbox, crs = "EPSG:28992")
res(rn) <- 500

r1_resampled <- resample(r1, rn)
r2_resampled <- resample(r2, rn)

m <- mosaic(sprc(r1_resampled, r2_resampled), fun = "last") # DHL should be last!
m[m == 0] <- NA
plot(m)
writeRaster(m, "data/beam_blockage/NL_beamblockage.tif", overwrite = TRUE)
```
# Quantifying seasonal cumulative migration
We use the vertical profiles to quantify how many birds actually pass over the Netherlands seasonally.

```{r}
vp_grid <- expand_grid(
  radar = c("HRW", "DHL"),
  year = c(2017:2023),
  month = c(2, 3, 4, 5, 8, 9, 10, 11)
)

vpfiles_to_vpts <- function(radar, year, month) {
  # print(paste0("data/vp/", radar, "/", year, "/", sprintf("%02d", month), "/*/*.h5"))
  rds_out <- paste0("data/vpts/", radar, year, sprintf("%02d", as.numeric(month)), ".RDS")
  if(file.exists(rds_out)) {
    print(paste0(rds_out, " exists"))
    return(rds_out)
  }
  vpfiles <- Sys.glob(paste0("data/vp/", radar, "/", year, "/", sprintf("%02d", as.numeric(month)), "/*/*.h5"))
  if (length(vpfiles) == 0) {
    return(paste0(rds_out, " skipped, no vpfiles"))
  }
  vps <- pbmclapply(vpfiles, function(x) {
    vp <- bioRad:::read_vp(x)
    vp
  }, mc.cores = 8)
  vps <- vps[!sapply(vps, is.null)] # Remove nulls
  vps <- do.call(bioRad:::c.vp, vps)
  
  vpts <- bind_into_vpts(vps)
  vpts <- regularize_vpts(vpts)
  sd_vvp_threshold(vpts) <- 2
  
  saveRDS(vpts, rds_out)
  print(paste0(rds_out, " processed"))
  return(rds_out)
}

out <- apply(vp_grid, 1, function(x) vpfiles_to_vpts(x[1], x[2], x[3]))

vptsfiles_to_mt <- function(radar, year) {
  year_vpts <- Sys.glob(paste0("data/vpts/", radar, year, "*.RDS"))
  
  year_vpts <- lapply(year_vpts, readRDS)
  year_vpts <- do.call(bind_into_vpts, year_vpts)
  # year_vpts <- regularize_vpts(year_vpts)
  
  spring_period <- c(paste0(year, "-02-15 00:00"), paste0(year, "-05-31 23:55"))
  autumn_period <- c(paste0(year, "-08-15 00:00"), paste0(year, "-11-30 23:55"))
  
  spring_vpts <- regularize_vpts(filter_vpts(year_vpts, spring_period[[1]], spring_period[[2]], night = TRUE), 
                                 date_min = as.POSIXct(spring_period[[1]]), date_max = as.POSIXct(spring_period[[2]]),
                                 interval = 300, fill = 3600)
  saveRDS(spring_vpts, paste0("data/vpts_seasonal/", radar, year, "_spring.RDS"))
  autumn_vpts <- regularize_vpts(filter_vpts(year_vpts, autumn_period[[1]], autumn_period[[2]], night = TRUE), 
                                 date_min = as.POSIXct(autumn_period[[1]]), date_max = as.POSIXct(autumn_period[[2]]),
                                 interval = 300, fill = 3600)
  saveRDS(autumn_vpts, paste0("data/vpts_seasonal/", radar, year, "_autumn.RDS"))
  spring_vpi <- integrate_profile(spring_vpts)
  autumn_vpi <- integrate_profile(autumn_vpts)
  
  cum_mt <- list("radar" = radar, "year" = year, "spring_mt" = max(spring_vpi$mt, na.rm = TRUE), "autumn_mt" = max(autumn_vpi$mt, na.rm = TRUE))
  return(cum_mt)
}

vpts_grid <- expand_grid(
  radar = c("HRW", "DHL"),
  year = c(2017:2023)
)

cum_mts <- pbmclapply(asplit(vpts_grid, 1), function(x) vptsfiles_to_mt(x[1], x[2]), mc.cores = 5)
saveRDS(cum_mts, "data/vpts/cum_mts.RDS")
```

```{r}
cum_mts <- readRDS("data/vpts/cum_mts.RDS")
cum_mts <- bind_rows(cum_mts) %>%
  pivot_longer(cols = c(spring_mt, autumn_mt), names_to = "season", values_to = "mt") %>%
  mutate(season = case_match(
    season,
    "autumn_mt" ~ "autumn",
    "spring_mt" ~ "spring"
  )) %>%
  filter(!(season == "spring" & year == 2017) & !(season == "autumn" & year == 2023))

cum_mts
```
And now we calculate averages from both radars combined for both spring and autumn.

```{r}
cum_mts %>%
  group_by(season) %>%
  summarise(mt_mean = mean(mt)) %>%
  arrange(season) %>%
  identity() -> mig_averages

cum_mts %>%
  group_by(season, radar) %>%
  summarise(mt_mean = mean(mt)) %>%
  arrange(radar, season) %>%
  identity() -> mig_averages_radar

cum_mts %>%
  group_by(season) %>%
  skim(mt)

cum_mts %>%
  group_by(season, radar) %>%
  skim(mt)
```

# Final maps

With all that data in place, we can start to compile the figures. The altitude profile figures  Figure 1  are in the radar-profiles.Rmd file.

## Figure data prep

```{r}
ban_dens <- rast("data/final_maps/NL_autumn_night_thresh_250_s_4_n_25_2h30m.tif")
bsn_dens <- rast("data/final_maps/NL_spring_night_thresh_250_s_4_n_25_2h30m.tif")

ban <- ban_dens
bsn <- bsn_dens

ban <- ban / global(ban, mean, na.rm = TRUE)[[1]]
bsn <- bsn / global(bsn, mean, na.rm = TRUE)[[1]]

ban <- ban * mig_averages$mt_mean[[1]]
bsn <- bsn * mig_averages$mt_mean[[2]]

c <- st_crs(ban)
nl <- geojsonsf::geojson_sf("data/gis/Netherlands.geojson") %>% st_transform(c)
nl_buf <- geojsonsf::geojson_sfc("data/gis/Netherlands-5km-Buffer.geojson") %>% st_transform(c)
clut_buf <- rast("data/final_maps/NL_autumn_night_thresh_250_s_4_n_25_clutter.tif") %>%
  as.polygons() %>%
  st_as_sf() %>%
  st_transform(c)
clut_man <- geojsonsf::geojson_sf("data/gis/manual_clutter.geojson") %>% st_transform(c) %>% filter(id < 5)

wpr <- rast("data/gis/NLD_power-density_100m.tif") %>% 
  project(ban) %>%
  resample(ban, method = "average")

bb <- rast("data/beam_blockage/NL_beamblockage.tif")
bb[bb < 0.05] <- NA
bb <- bb %>%
  as.polygons() %>%
  simplifyGeom(1000) %>%
  fillHoles() %>%
  st_as_sf() %>%
  st_transform(c)
bb$pattern <- "stripe"
nhol <- geojsonsf::geojson_sfc("data/gis/Noord-Holland.geojson") %>% st_transform(c)
nhol_buf <- geojsonsf::geojson_sfc("data/gis/Noord-Holland-10km-Buffer.geojson") %>% st_transform(c)
nhol_bbox <- st_bbox(nhol_buf)
radar_buf <- geojsonsf::geojson_sf("data/gis/Radars-100km-Buffer.geojson") %>% st_transform(c)
radars <- geojsonsf::geojson_sf("data/gis/Radars.geojson") %>% st_transform(c) %>% filter(acronym != "artis")

gebieden <- geojsonsf::geojson_sf("data/gis/gemeenten.geojson") %>% st_transform(c) %>% 
  filter(Gemeentenaam %in% c("Amsterdam", "Diemen")) %>%
  rename(gebied = Gemeentenaam) %>%
  dplyr::select(gebied, geometry) %>%
  bind_rows(nhol %>% st_as_sf() %>% rename(geometry = x) %>% mutate(gebied = "Noord-Holland")) %>%
  bind_rows(nl %>% mutate(gebied = "Nederland") %>% dplyr::select(gebied, geometry))

bbc <- st_geometry(bb) %>% st_intersection(st_geometry(nl_buf))
clut_bufc <- st_geometry(clut_buf) %>% st_intersection(st_geometry(nl_buf))
clut_manc <- st_geometry(clut_man) %>% st_intersection(st_geometry(nl_buf))
uncertainty <- spatialEco::sf_dissolve(st_as_sf(st_union(st_union(bbc, clut_bufc), clut_manc)))
uncertainty$certainty <- "Clutter affected"

res_all <- st_read("data/gis/RES/RES_zoekgebieden_Actueel.shp") %>%
  nrow() %>%
  print()

res_all <- st_read("data/gis/RES/RES_zoekgebieden_Actueel.shp") %>%
  filter(str_detect(`Type_`, 'Wind') | str_detect(`Type_`, 'wind')) %>% 
  st_transform(c)
res_all %>%
  sf:::select.sf(RES_id, Naam_gebie, Type_, Regio, RES_deel_r) %>%
  st_difference(clut_bufc) %>%  # Remove areas in clutter contaminated zone
  mutate(Naam_gebie = str_replace(Naam_gebie, "\\d+[a-z]\\) ", ""),
         ID = row_number()) %>%
  identity() -> res

turbine_all <- st_read("data/gis/rivm_20250101_windturbines_ashoogte.shp") %>%
  st_transform(c) %>%
  st_intersection(st_geometry(nl_buf)) %>%
  st_difference(clut_bufc)

turbine_nhol <- st_read("data/gis/rivm_20250101_windturbines_ashoogte.shp") %>%
  st_transform(c) %>%
  st_intersection(st_geometry(nhol)) %>%
  st_difference(clut_bufc)

radar_buf %>%
  st_intersection(nl_buf) %>%
  st_difference(clut_bufc) %>%
  spatialEco::sf_dissolve() %>%
  identity() -> nl_clut

nhol %>%
  st_difference(clut_bufc) %>%
  identity() -> nhol_clut

ban_extract <- terra::extract(ban, vect(res), raw = TRUE) %>% as.data.frame() %>% rename(MT_autumn = focal_mean)
bsn_extract <- terra::extract(bsn, vect(res), raw = TRUE) %>% as.data.frame() %>% rename(MT_spring = focal_mean)
wpr_extract <- terra::extract(wpr, vect(res), raw = TRUE) %>% as.data.frame() %>% rename(power_density = `NLD_power-density_100m`)

trb_ban_extract <- terra::extract(ban, vect(turbine_all), raw = TRUE) %>% as.data.frame() %>% rename(MT_autumn = focal_mean)
trb_bsn_extract <- terra::extract(bsn, vect(turbine_all), raw = TRUE) %>% as.data.frame() %>% rename(MT_spring = focal_mean)
trb_wpr_extract <- terra::extract(wpr, vect(turbine_all), raw = TRUE) %>% as.data.frame() %>% rename(power_density = `NLD_power-density_100m`)

trb_ban_nhol <- terra::extract(ban, vect(turbine_nhol), raw = TRUE) %>% as.data.frame() %>% rename(MT_autumn = focal_mean)
trb_bsn_nhol <- terra::extract(bsn, vect(turbine_nhol), raw = TRUE) %>% as.data.frame() %>% rename(MT_spring = focal_mean)
trb_wpr_nhol <- terra::extract(wpr, vect(turbine_nhol), raw = TRUE) %>% as.data.frame() %>% rename(power_density = `NLD_power-density_100m`)

ban_nhol <- terra::extract(ban, vect(nhol_clut), raw = TRUE) %>% as.data.frame() %>% rename(MT_autumn = focal_mean)
bsn_nhol <- terra::extract(bsn, vect(nhol_clut), raw = TRUE) %>% as.data.frame() %>% rename(MT_spring = focal_mean)
wpr_nhol <- terra::extract(wpr, vect(nhol_clut), raw = TRUE) %>% as.data.frame() %>% rename(power_density = `NLD_power-density_100m`)

ban_nl <- terra::extract(ban, vect(nl_clut), raw = TRUE) %>% as.data.frame() %>% rename(MT_autumn = focal_mean)
bsn_nl <- terra::extract(bsn, vect(nl_clut), raw = TRUE) %>% as.data.frame() %>% rename(MT_spring = focal_mean)
wpr_nl <- terra::extract(wpr, vect(nl_clut), raw = TRUE) %>% as.data.frame() %>% rename(power_density = `NLD_power-density_100m`)

nhol_average_ban <- terra::extract(ban, vect(nhol_clut), raw = TRUE) %>% as.data.frame() %>% summarise(avg = mean(focal_mean, na.rm = TRUE))
nhol_average_bsn <- terra::extract(bsn, vect(nhol_clut), raw = TRUE) %>% as.data.frame() %>% summarise(avg = mean(focal_mean, na.rm = TRUE))
```

```{r}
terra::extract(ban_dens, vect(nl_clut), raw = TRUE) %>% as.data.frame() %>% mutate(focal_mean = focal_mean / 11) %>% skim(focal_mean) # summarise(avg = mean(focal_mean, na.rm = TRUE))
terra::extract(bsn_dens, vect(nl_clut), raw = TRUE) %>% as.data.frame() %>% mutate(focal_mean = focal_mean / 11) %>% skim(focal_mean) # summarise(avg = mean(focal_mean, na.rm = TRUE))
```

```{r}
terra::extract(ban, vect(nl_clut), raw = TRUE) %>% as.data.frame() %>% skim(focal_mean) # summarise(avg = mean(focal_mean, na.rm = TRUE))
terra::extract(bsn, vect(nl_clut), raw = TRUE) %>% as.data.frame() %>% skim(focal_mean)
# print(paste0("Average bird density spring: ", nl_average_bsn / 11))  # Outside of clutter areas
# print(paste0("Average bird density autumn: ", nl_average_ban / 11))
```

## Figure 2: Overview maps of the Netherlands

```{r message=FALSE, warning=FALSE}
nl_buf_spatvector <- vect(nl_buf)

ban <- terra::mask(ban, nl_buf_spatvector)
bsn <- terra::mask(bsn, nl_buf_spatvector)

map_to_df <- function(map, s, d, z) {
  as.data.frame(map, xy = TRUE) %>%
    rename("mt_mean" = "focal_mean") %>%
    mutate(mt_mean = mt_mean / 1000,
           season = s,
           daytime = d,
           zlim = z)
}

data <- mapply(map_to_df, map = list(ban, bsn), 
               s = c("Autumn", "Spring"), 
               d = c("night", "night"),
               z = c(800, 800),
               SIMPLIFY = FALSE) %>%
  bind_rows()
  
data %>%
  # filter(daytime == "night", season == "Autumn") %>%
  ggplot() +
  geom_sf(data = nl, fill = "NA", color = alpha("black", 0.5), linewidth = .3) +
  geom_raster(aes(x = x, y = y, fill = mt_mean)) +
  scale_fill_viridis_c(limits = c(0, 900), oob = scales::squish, option = "inferno", na.value = 0,
                       name = expression(atop("Migration traffic", "\u00D7" ~ 1000 ~ "birds" %.% "km"^-1))) +
  theme_void(base_size = 14) +
  geom_sf(data = nl_buf, fill = "NA", color = alpha("white", 0.9), linewidth = 2) +
  geom_sf(data = st_union(radar_buf), fill = "NA", color = alpha("white", 0.9), linewidth = 2) +
  geom_sf(data = nl, fill = "NA", color = alpha("white", 0.3), linewidth = .3) +
  # geom_sf(data = nl_buf, fill = "NA", color = "white", linewidth = .3) +
  geom_sf(data = nhol, fill = "NA", color = alpha("white", 0.3), linewidth = .3) +
  geom_sf(data = radar_buf, fill = "NA", color = alpha("white", 0.3), linewidth = .3) +
  # geom_sf(data = uncertainty %>% st_intersection(radar_buf %>% st_buffer(-1000)) %>% st_intersection(nl_buf), fill = "#00000025", 
  #         color = alpha("white", 0.3), linewidth = .3) +
  geom_sf_pattern(aes(pattern = certainty),
                  data = uncertainty %>% st_intersection(st_union(radar_buf) %>% st_buffer(-1000)) %>% st_intersection(nl_buf),
                  fill = alpha("black", 0.15), color = alpha("black", 0.15),
                  pattern_density = 0.3, pattern_spacing = 0.005, pattern_fill = alpha("black", 0.1), pattern_color = NA) +
  geom_sf(data = radars, color = alpha("white", 0.5), size = 3) +
  scale_pattern_manual(values = "stripe", name = "Clutter affected") +
  coord_sf(expand = FALSE) +
  facet_wrap(~fct_relevel(season, "Spring", "Autumn")) +
  annotation_scale(text_col = "black", style = "ticks", line_col = "black") +
  theme(panel.spacing.x = unit(0, "lines"),
        legend.position = "bottom", 
        legend.key.width = unit(1.5, "cm"))
ggsave("data/final_maps_plots/maps.pdf", width = 17, height = 10, device = cairo_pdf)
```

## Figure 3a: Overview map of North-Holland

```{r message=FALSE, warning=FALSE}
nhol_bbox_expanded <- nhol_bbox
padding <- -5000
nhol_bbox_expanded["xmin"] <- nhol_bbox_expanded["xmin"] - padding - 20000
nhol_bbox_expanded["xmax"] <- nhol_bbox_expanded["xmax"] + padding
nhol_bbox_expanded["ymin"] <- nhol_bbox_expanded["ymin"] - padding
nhol_bbox_expanded["ymax"] <- nhol_bbox_expanded["ymax"] + padding + 30000

pol_bbox <- st_as_sf(st_as_sfc(st_bbox(nhol_bbox_expanded)))
pol_nhol <- nhol_buf

nhol_outside_mask <- st_difference(pol_bbox, pol_nhol)

data %>%
  filter(daytime == "night", season == "Autumn") %>%
  ggplot() +
  geom_sf(data = nl, fill = "NA", color = alpha("black", 0.5), linewidth = .3) +
  geom_raster(aes(x = x, y = y, fill = mt_mean)) +
  scale_fill_viridis_c(limits = c(0, 900), oob = scales::squish, option = "inferno", na.value = 0,
                       name = expression(atop("Migration traffic", "\u00D7" ~ 1000 ~ "birds" %.% "km"^-1))) +
  theme_void(base_size = 14) +
  geom_sf(data = nl_buf, fill = "NA", color = alpha("white", 1), linewidth = 4) +
  geom_sf(data = st_union(radar_buf), fill = "NA", color = alpha("white", 0.9), linewidth = 2) +
  geom_sf(data = nl, fill = "NA", color = alpha("white", 0.3), linewidth = .3) +
  # geom_sf(data = nl_buf, fill = "NA", color = "white", linewidth = .3) +
  geom_sf(data = nhol, fill = "NA", color = alpha("white", 0.3), linewidth = .3) +
  geom_sf(data = radar_buf, fill = "NA", color = alpha("white", 0.3), linewidth = .3) +
  # geom_sf(data = uncertainty %>% st_intersection(radar_buf %>% st_buffer(-1000)) %>% st_intersection(nl_buf), fill = "#00000025", 
  #         color = alpha("white", 0.3), linewidth = .3) +
  # geom_sf_pattern(aes(pattern = certainty),
  #                 data = uncertainty %>% st_intersection(radar_buf %>% st_buffer(-1000)) %>% st_intersection(nl_buf),
  #                 fill = alpha("white", 0.15), color = alpha("black", 0.1),
  #                 pattern_density = 0.025, pattern_spacing = 0.01, pattern_fill = alpha("black", 0.1), show.legend = TRUE) +
  geom_sf_pattern(aes(pattern = certainty),
                  data = uncertainty %>% st_intersection(st_union(radar_buf) %>% st_buffer(-1000)) %>% st_intersection(nl_buf),
                  fill = alpha("black", 0.15), color = alpha("black", 0.15),
                  pattern_density = 0.3, pattern_spacing = 0.01, pattern_fill = alpha("black", 0.1), pattern_color = NA,
                  show.legend = TRUE) +
  geom_sf(data = radars, color = alpha("white", 0.5), size = 2.5) +
  new_scale_fill() +
  new_scale_color() +
  geom_sf(data = res, aes(fill = "Candidate sites", color = "Candidate sites"), linewidth = 0.3, show.legend = TRUE) +
  scale_fill_manual(values = alpha("yellow", 0.85), name = "Candidate sites") +
  scale_color_manual(values = alpha("black", 0.85), name = "Candidate sites") +
  scale_pattern_manual(values = "stripe", name = "Clutter affected") +
  # geom_sf(data = nhol_outside_mask, fill = alpha("black", 0.6), color = NA) +
  coord_sf(xlim = c(nhol_bbox_expanded["xmin"], nhol_bbox_expanded["xmax"]),
           ylim = c(nhol_bbox_expanded["ymin"], nhol_bbox_expanded["ymax"]),
           expand = FALSE) +
  # facet_wrap(~fct_relevel(season, "Spring", "Autumn")) +
  annotation_scale(text_col = "black", style = "ticks", line_col = "black") +
  theme(panel.margin.x = unit(0, "lines"))

ggsave("data/final_maps_plots/northholland.pdf", width = 8, height = 10, device = cairo_pdf)
```

## Figure 3b: Migration across candidate sites

```{r}
ban_extract %>%
  cbind(bsn_extract %>% dplyr::select(MT_spring)) %>%
  cbind(wpr_extract %>% dplyr::select(power_density)) %>%
  left_join(res, by = "ID") %>%
  arrange(desc(MT_autumn)) %>%
  mutate(Naam_gebie = case_match(Naam_gebie,
                                "Knooppunt Holendrecht" ~ "Holendrecht",
                                "Diemen Wind B" ~ "Diemen B",
                                "Diemen Wind C" ~ "Diemen C",
                                "IJburg Diemerpark" ~ "IJburg Diemerp.",
                                "Zeeburgereiland" ~ "Zeeburgereil.",
                                "Havengebied West" ~ "Havengeb. West",
                                "Zuiderlegmeerpolder-oost" ~ "Zuiderlegmeerp.",
                                "Kade Velsen Noord" ~ "Velsen Noord",
                                "ten noorden ring A10 - westelijk gebied" ~ "Ring A10 Noord W",
                                "ten noorden ring A10" ~ "Ring A10 Noord",
                                "Zon en wind in  Noordzeekanaalgebied" ~ "Z&W Noordzknl.",
                                "Waterleidingenterrein / Gein" ~ "Waterl. / Gein",
                                "Strandeiland/Buiteneiland West" ~ "Buiteneil. West",
                                .default = Naam_gebie),
         Naam_gebie = as.factor(Naam_gebie),
         Naam_gebie = fct_reorder(Naam_gebie, MT_autumn),
         geometry_x = st_coordinates(st_centroid(geometry))[,1],
         geometry_y = st_coordinates(st_centroid(geometry))[,2]) %>%
  group_by(Naam_gebie) %>%
  mutate(MT_mean_autumn = mean(MT_autumn),
         MT_mean_spring = mean(MT_spring)) %>%
  ungroup() %>%
  group_by(RES_deel_r) %>%
  mutate(mean_x = mean(geometry_x),
         mean_y = mean(geometry_y),
         RES_deel_r = as.factor(RES_deel_r),
         RES_deel_r = fct_reorder(RES_deel_r, mean_y, .desc = FALSE),
         RES_deel_r = recode(RES_deel_r,
                             "Regio Alkmaar" = "Alkmaar",
                             "West-Friesland" = "West-Friesland",
                             "IJmond-Zuid Kennemerland" = "IJmond/\nZuid-Kennemerland",
                             "Zaanstreek-Waterland" = "Zaanstreek/\nWaterland",
                             "Amsterdam" = "Amsterdam",
                             "Amstelland" = "Amstelland",
                             "Haarlemmermeer" = "Haarlemmermeer")) %>%
  ungroup() %>%
  identity() -> res_summaries

key <- legendry::key_range_manual(start = c(min(res_summaries$MT_spring) / 1000, min(res_summaries$MT_autumn) / 1000),
                        end = c(max(res_summaries$MT_spring) / 1000, max(res_summaries$MT_autumn) / 1000),
                        name = c("Spring", "Autumn"))

print(terra::extract(bsn, vect(nhol_clut), raw = TRUE) %>% skim(focal_mean))
print(terra::extract(ban, vect(nhol_clut), raw = TRUE) %>% skim(focal_mean))

print(res_summaries %>% skim(MT_autumn))
print(res_summaries %>% skim(MT_spring))

res_summaries %>%
  ggplot() +
  geom_vline(color = "#00000075", xintercept = nhol_average_ban[[1]] / 1000, linetype = "longdash") +
  geom_vline(color = "#00000075", xintercept = nhol_average_bsn[[1]] / 1000, linetype = "longdash") +
  ggdist::stat_pointinterval(aes(x = MT_autumn / 1000, y = Naam_gebie, color = MT_mean_autumn / 1000), .width = c(1, .5)) +
  ggdist::stat_pointinterval(aes(x = MT_spring / 1000, y = Naam_gebie, color = MT_mean_spring / 1000), .width = c(1, .5)) +
  scale_color_viridis_c(name = "birds/km", option = "inferno", end = 0.85, breaks = c(0, 250, 500, 750), limits = c(0, 900)) +
  scale_y_discrete(breaks = levels(res_summaries$Naam_gebie)[seq(1, length(levels(res_summaries$Naam_gebie)), by = 2)]) +
  guides(#x.sec = guide_axis_nested(key = key, bracket = "square"),
         x.sec = legendry::guide_axis_nested(key, bracket = "square"),
         color = guide_colorbar(title = expression(atop("Migration traffic", "\u00D7" ~ 1000 ~ "birds" %.% "km"^-1)),
                                direction = "vertical",
                                barwidth = 1.2,
                                barheight = 10,
                                position = "inside",
                                draw.ulim = TRUE)) +
  theme_minimal(base_size = 14) +
  theme(strip.text.y.right = element_text(angle = 0),
        axis.title.x = element_text(hjust = 1),
        legend.direction = "vertical",
        legend.background = element_rect(fill = "white", colour = NA),
        legend.position = "right",
        legend.position.inside = c(0.85, 0.3),
        legend.title = element_text(hjust = 0),
        legend.key.width = unit(0.7, "inches"),
        legend.key.height = unit(0.2, "inches")) +
  labs(# title = "Seasonal migration traffic",
       # subtitle = "across candidate sites for wind energy in the province of North-Holland",
       x = expression("\u00D7" ~ 1000 ~ "birds" %.% "km"^-1),
       y = "Candidate site") +
  coord_cartesian(xlim = c(150, 825), expand = FALSE)
ggsave(filename = "data/final_maps_plots/candidatesites.pdf", width = 8, height = 6)

res_summaries %>%
  ggplot() +
  geom_vline(color = "#00000075", xintercept = nhol_average_ban[[1]] / 1000, linetype = "longdash") +
  geom_vline(color = "#00000075", xintercept = nhol_average_bsn[[1]] / 1000, linetype = "longdash") +
  ggdist::stat_pointinterval(aes(x = MT_autumn / 1000, y = Naam_gebie, color = MT_mean_autumn / 1000), .width = c(1, .5)) +
  ggdist::stat_pointinterval(aes(x = MT_spring / 1000, y = Naam_gebie, color = MT_mean_spring / 1000), .width = c(1, .5)) +
  scale_color_viridis_c(name = "birds/km", option = "inferno", end = 0.85, breaks = c(0, 250, 500, 750), limits = c(0, 900)) +
  # scale_y_discrete(breaks = levels(res_summaries$Naam_gebie)[seq(1, length(levels(res_summaries$Naam_gebie)), by = 2)]) +
  guides(#x.sec = guide_axis_nested(key = key, bracket = "square"),
         x.sec = legendry::guide_axis_nested(key, bracket = "square"),
         color = guide_colorbar(title = expression(atop("Migration traffic", "\u00D7" ~ 1000 ~ "birds" %.% "km"^-1)),
                                direction = "vertical",
                                barwidth = 1.2,
                                barheight = 10,
                                position = "inside",
                                draw.ulim = TRUE)) +
  theme_minimal(base_size = 14) +
  theme(strip.text.y.right = element_text(angle = 0),
        axis.title.x = element_text(hjust = 1),
        legend.direction = "vertical",
        legend.background = element_rect(fill = "white", colour = NA),
        legend.position = "right",
        legend.position.inside = c(0.85, 0.3),
        legend.title = element_text(hjust = 0),
        legend.key.width = unit(0.7, "inches"),
        legend.key.height = unit(0.2, "inches")) +
  labs(# title = "Seasonal migration traffic",
       # subtitle = "across candidate sites for wind energy in the province of North-Holland",
       x = expression("\u00D7" ~ 1000 ~ "birds" %.% "km"^-1),
       y = "Candidate site") +
  coord_cartesian(xlim = c(150, 825), expand = FALSE)
ggsave(filename = "data/final_maps_plots/candidatesites_all.pdf", width = 8, height = 12)
```

## Figure 3c: Power density - North-Holland

```{r}
ban_crop_nhol <- terra::mask(ban, vect(nhol)) %>% as.data.frame(xy = TRUE) %>% rename(MT_autumn = focal_mean)
wpr_crop_nhol <- terra::mask(wpr, vect(nhol)) %>% as.data.frame(xy = TRUE) %>% rename(power_density = `NLD_power-density_100m`)
mapdata <- left_join(ban_crop_nhol, wpr_crop_nhol, by = join_by(x, y))
reverse_nhol <- st_difference(st_as_sfc(nhol_bbox), st_union(nhol))

round_any <- function(x, accuracy, f = round){f(x / accuracy) * accuracy}

mapdata %>%
  mutate(MT_autumn_disp = round_any(MT_autumn, 25000),
         power_density_disp = round_any(power_density, 25)) %>%
  bi_class(x = "MT_autumn_disp", y = "power_density_disp", "equal", dim = 4) %>%
  identity() -> data

data <- bi_class(mapdata, x = "MT_autumn", y = "power_density", "equal", dim = 4)

nhol_simple <- rmapshaper::ms_simplify(nhol, keep = 0.07)

map <- ggplot() +
  geom_raster(data = data, mapping = aes(x = x, y = y, fill = bi_class), show.legend = FALSE) +  
  geom_sf(data = reverse_nhol, fill = "white", color = NA) +
  bi_scale_fill(pal = "DkViolet2", dim = 4) +
  geom_sf_pattern(aes(pattern = certainty),
                  data = uncertainty %>% st_intersection(nhol_simple),
                  fill = alpha("black", 0.2), color = alpha("black", 0.2),
                  pattern_density = 0.3, pattern_spacing = 0.01, pattern_fill = alpha("black", 0.15), pattern_color = NA,
                  show.legend = TRUE) +
  geom_sf(data = radars, color = alpha("white", 0.5), size = 2.5) +
  geom_sf(data = res, linewidth = 0.3, fill = "red", color = "white") +
  coord_sf(expand = FALSE) +
  # facet_wrap(~fct_relevel(season, "Spring", "Autumn")) +
  annotation_scale(text_col = "black", style = "ticks", line_col = "black") +
  labs() +
  guides(fill = "none") +
  theme_void()

map

legend <- bi_legend(pal = "DkViolet2",
                    dim = 4,
                    xlab = "Migration passage ",
                    ylab = "Wind power density ",
                    size = 8)
```

```{r}
bind_cols(wpr_extract, ban_extract, bsn_extract) %>%
  dplyr::select(ID = `ID...1`, power_density, MT_autumn, MT_spring) %>%
  pivot_longer(cols = c(MT_autumn, MT_spring), names_to = "season", values_to = "MT") %>%
  mutate(season = case_when(season == "MT_autumn" ~ "Autumn",
                            season == "MT_spring" ~ "Spring"),
         type = "Candidate sites") %>%
  identity() -> wpr_res_nhol
  
bind_cols(wpr_nhol, ban_nhol, bsn_nhol) %>%
  dplyr::select(power_density, MT_autumn, MT_spring) %>%
  pivot_longer(cols = c(MT_autumn, MT_spring), names_to = "season", values_to = "MT") %>%
  mutate(season = case_when(season == "MT_autumn" ~ "Autumn",
                            season == "MT_spring" ~ "Spring"),
         type = "Background") %>%
  identity() -> wpr_bkg_nhol

bind_rows(wpr_bkg_nhol, wpr_res_nhol) %>%
  mutate(season = fct_relevel(season, c("Spring", "Autumn")),
         MT = MT / 1000,
         MT_disp = round_any(MT, 25) + 25/2,
         power_density_disp = round_any(power_density, 25) + 25/2) %>%
  # bi_class(x = "MT", y = "power_density", "equal", dim = 4) %>%
  bi_class(x = "MT_disp", y = "power_density_disp", "equal", dim = 4) %>%
  identity() -> wpr_data

wpr_means <- wpr_data %>%
  group_by(season) %>%
  summarise(MT_mean = mean(MT, na.rm = TRUE),
            pd_mean = mean(power_density, na.rm = TRUE))

wpr_means_res <- wpr_data %>%
  left_join(res, by = "ID") %>%
  # filter(type == "Candidate sites", season == "Autumn") %>%
  mutate(Naam_gebie = case_match(Naam_gebie,
                              "Knooppunt Holendrecht" ~ "Holendrecht",
                              "Diemen Wind B" ~ "Diemen B",
                              "Diemen Wind C" ~ "Diemen C",
                              "IJburg Diemerpark" ~ "IJburg Diemerp.",
                              "Zeeburgereiland" ~ "Zeeburgereil.",
                              "Havengebied West" ~ "Havengeb. West",
                              "Zuiderlegmeerpolder-oost" ~ "Zuiderlegmeerp.",
                              "Kade Velsen Noord" ~ "Velsen Noord",
                              "ten noorden ring A10 - westelijk gebied" ~ "Ring A10 Noord W",
                              "ten noorden ring A10" ~ "Ring A10 Noord",
                              "Zon en wind in  Noordzeekanaalgebied" ~ "Z&W Noordzknl.",
                              "Waterleidingenterrein / Gein" ~ "Waterl. / Gein",
                              "Strandeiland/Buiteneiland West" ~ "Buiteneil. West",
                              .default = Naam_gebie),
         Naam_gebie = case_match(Naam_gebie,
                                 # "Z&W Noordzknl." ~ "Z&W Noordzknl.",
                                 # "Strandeiland/Buiteneiland Oost" ~ "Strandeiland/Buiteneiland Oost",
                                 "Landelijk Noord" ~ "Landelijk Noord",
                                 "Oosterwijzend" ~ "Oosterwijzend",
                                 # "Amsterdam-Zuid - Kop van Amstelscheg" ~ "Amsterdam-Zuid - Kop van Amstelscheg",
                                 # "Alton" ~ "Alton",
                                 .default = NULL),
       Naam_gebie = as.factor(Naam_gebie)) %>%
  group_by(season, ID, type, Naam_gebie) %>%
  summarise(MT_mean = mean(MT, na.rm = TRUE),
            pd_mean = mean(power_density, na.rm = TRUE),
            area_size = n()) %>%
  identity()

wpr_means_res <- wpr_means_res %>%
  filter(!type == "Background") %>%
  group_by(season) %>%
  bi_class(x = "MT_mean", y = "pd_mean", "equal", dim = 4)

distrib <- ggplot() +
  geom_raster(aes(x = MT_disp, y = power_density_disp, fill = bi_class),
              data = wpr_data %>% filter(type == "Background") %>%
                dplyr::select(MT_disp, power_density_disp, season, bi_class) %>%
                distinct(),
              hjust = 0, vjust = 0, show.legend = FALSE) +
  geom_vline(data = wpr_means, aes(xintercept = MT_mean), color = "white", linewidth = 0.75) +
  geom_hline(data = wpr_means, aes(yintercept = pd_mean), color = "white", linewidth = 0.75) +
  geom_point(aes(x = MT_mean, y = pd_mean, size = area_size), data = wpr_means_res, pch = 21, fill = "red", color = "white", stroke = 1.5) +
  bi_scale_fill(pal = "DkViolet2", dim = 4) +
  geom_label_repel(aes(x = MT_mean, y = pd_mean, label = Naam_gebie), data = wpr_means_res, min.segment.length = 0, force = 100) +
  theme_light(base_size = 14) +
  scale_x_continuous(breaks = c(0, 200, 400, 600, 800)) +
  scale_size(range = c(2, 8)) +
  scale_y_continuous(n.breaks = 4) +
  # coord_cartesian(expand = FALSE, ) +
  coord_fixed(ratio = 1) +
  labs(x = "Migration passage [birds/km]",
       y = "Wind power density [W/m2]") +
  guides(size = "none") +
  facet_wrap(vars(season), axes = "all_x", axis.labels = "all_x")

distrib

finalplot <- ggdraw() +
  draw_plot(map, 0, 0, 1, 1) +
  draw_plot(legend, 0.1, .65, 0.2, 0.2)
```

```{r}
ggsave(filename = "data/plots/powerdens_vs_migpassage_map.pdf", plot = finalplot, width = 8, height = 7.5)
ggsave(filename = "data/plots/powerdens_vs_migpassage_distrib.pdf", plot = distrib, width = 15, height = 7.5)
```

## Figure 3d: Power density - Netherlands

```{r}
bind_cols(trb_wpr_extract, trb_ban_extract, trb_bsn_extract) %>%
  dplyr::select(ID = `ID...1`, power_density, MT_autumn, MT_spring) %>%
  pivot_longer(cols = c(MT_autumn, MT_spring), names_to = "season", values_to = "MT") %>%
  mutate(season = case_when(season == "MT_autumn" ~ "Autumn",
                            season == "MT_spring" ~ "Spring"),
         type = "Existing sites") %>%
  identity() -> wpr_trb
  
bind_cols(wpr_nl, ban_nl, bsn_nl) %>%
  dplyr::select(power_density, MT_autumn, MT_spring) %>%
  pivot_longer(cols = c(MT_autumn, MT_spring), names_to = "season", values_to = "MT") %>%
  mutate(season = case_when(season == "MT_autumn" ~ "Autumn",
                            season == "MT_spring" ~ "Spring"),
         type = "Background") %>%
  identity() -> wpr_bkg

bind_cols(wpr_extract, ban_extract, bsn_extract) %>%
  dplyr::select(power_density, MT_autumn, MT_spring) %>%
  pivot_longer(cols = c(MT_autumn, MT_spring), names_to = "season", values_to = "MT") %>%
  mutate(season = case_when(season == "MT_autumn" ~ "Autumn",
                            season == "MT_spring" ~ "Spring"),
         type = "Candidate sites") %>%
  identity() -> wpr_res

bind_rows(wpr_trb, wpr_bkg, wpr_res) %>%
  mutate(season = fct_relevel(season, c("Spring", "Autumn")),
         MT = MT / 1000) %>%
  identity() -> wpr_data

wpr_means <- wpr_data %>%
  group_by(season) %>%
  summarise(MT_mean = mean(MT, na.rm = TRUE),
            pd_mean = mean(power_density, na.rm = TRUE))

set.seed(42)
ggplot() +
  geom_bin_2d(aes(x = MT, y = power_density, fill = after_stat(ndensity)),
              data = wpr_data %>% filter(type == "Background") %>% dplyr::select(MT, power_density, season), bins = 25) +
  geom_hdr_lines(aes(x = MT, y = power_density, color = type),
                 data = wpr_data %>% filter(type %in% c("Existing sites", "Candidate sites")),
                 probs = c(0.95, 0.8, 0.5), show.legend = TRUE) +
  geom_vline(data = wpr_means, aes(xintercept = MT_mean), color = "white") +
  geom_hline(data = wpr_means, aes(yintercept = pd_mean), color = "white") +
  # geom_hline(yintercept = mean(wpr_data$power_density, na.rm = TRUE), color = "white") +
  # scale_alpha_manual(values = c(0.6, 0.8, 1)) +
  scale_color_manual(values = c("red", "white")) +
  scale_fill_viridis_c() +
  theme_minimal(base_size = 14) +
  scale_x_continuous(breaks = c(0, 200, 400, 600, 800)) +
  scale_y_continuous(n.breaks = 4) +
  # coord_cartesian(expand = FALSE, ) +
  coord_fixed(ratio = 0.904) +
  labs(x = "Migration passage [birds/km]",
       y = "Power density [W/m2]") +
  # guides(alpha = "none") +
  facet_wrap(vars(season, type), nrow = 1)
ggsave("powerdensity_vs_migpassage_nl.pdf", width = 17, height = 5)
```

# Statistics

Surface area of maps

```{r}
ar <- cellSize(ban, mask = TRUE)
covered_by_map <- global(ar, sum, na.rm = TRUE) / 1000000  # m2 to km2

# And as a proportion of the Netherlands
surface_nl <- 41540
covered_by_map / surface_nl
```
Nights with pulses identified

```{r}
unique_nights <- vp_mtr_cum50 %>%
  distinct(date_trunc) %>%
  identity() %>%
  nrow()

print(unique_nights)

# And per season
vp_mtr_cum50 %>% 
  group_by(season) %>% 
  distinct(date_trunc) %>%
  summarise(n_per_season = n())

# And averages per season
vp_mtr_cum50 %>%
  group_by(year, season) %>%
  distinct(date_trunc) %>%
  summarise(n_per_season = n()) %>%
  group_by(season) %>%
  dplyr::select(season, n_per_season) %>%
  skim()
```

Nights per season

```{r}
vp_mtr %>%
  filter(day_night == "night") %>%
  group_by(season, year, odim_code) %>%
  summarise(nights_per_season = n()) %>%
  group_by(season) %>%
  summarise(nights_per_season_max = max(nights_per_season))
```



```{r}
res_summaries %>%
  filter(Naam_gebie != "Landelijk Noord") %>%
  add_count(Naam_gebie) %>%
  mutate(above_average = if_else(MT_mean_autumn >= nhol_average_ban[[1]], "yes", "no"),
         above_90 = if_else(MT_mean_autumn >= quantile(MT_mean_autumn, .9), "yes", "no")) %>%
  group_by(above_average) %>%
  summarise(size = sum(n))
```

```{r}
cv <- function(data) { sd(data) / mean(data) * 100}

cv_spring <- cv(res_summaries$MT_spring)
cv_autumn <- cv(res_summaries$MT_autumn)
print(c(cv_spring, cv_autumn))
```

# Raw maps

```{r}
raw_a <- rast("data/maps/night/scans/NL_autumn_night_thresh_2500_avg_scans_10_2h30m.tif") %>% trim()
raw_s <- rast("data/maps/night/scans/NL_spring_night_thresh_2500_avg_scans_10_2h30m.tif") %>% trim()

nl_buf_spatvector <- vect(nl_buf)

ran <- terra::mask(raw_a, nl_buf_spatvector)
rsn <- terra::mask(raw_s, nl_buf_spatvector)

map_to_df <- function(map, s, d, z) {
  as.data.frame(map, xy = TRUE) %>%
    mutate(season = s,
           daytime = d,
           zlim = z)
}

data <- mapply(map_to_df, map = list(ran, rsn), 
               s = c("Autumn", "Spring"), 
               d = c("night", "night"),
               z = c(800, 800),
               SIMPLIFY = FALSE) %>%
  bind_rows()
  
data %>%
  # filter(daytime == "night", season == "Autumn") %>%
  ggplot() +
  geom_sf(data = nl, fill = "NA", color = alpha("black", 0.5), linewidth = .3) +
  geom_raster(aes(x = x, y = y, fill = vir_mean)) +
  scale_fill_viridis_c(limits = c(0, 900), oob = scales::squish, option = "inferno", na.value = 0,
                       name = "Vertically integrated reflectivity [cm^2]") +
  theme_void(base_size = 14) +
  geom_sf(data = nl_buf, fill = "NA", color = alpha("white", 0.9), linewidth = 2) +
  geom_sf(data = st_union(radar_buf), fill = "NA", color = alpha("white", 0.9), linewidth = 2) +
  geom_sf(data = nl, fill = "NA", color = alpha("white", 0.3), linewidth = .3) +
  # geom_sf(data = nl_buf, fill = "NA", color = "white", linewidth = .3) +
  geom_sf(data = nhol, fill = "NA", color = alpha("white", 0.3), linewidth = .3) +
  geom_sf(data = radar_buf, fill = "NA", color = alpha("white", 0.3), linewidth = .3) +
  geom_sf_pattern(aes(pattern = certainty),
                  data = uncertainty %>% st_intersection(st_union(radar_buf) %>% st_buffer(-1000)) %>% st_intersection(nl_buf),
                  fill = alpha("black", 0.50), color = alpha("white", 0.50),
                  pattern_density = 0.3, pattern_spacing = 0.005, pattern_fill = alpha("black", 0.1), pattern_color = NA) +
  geom_sf(data = radars, color = alpha("white", 0.5), size = 3) +
  scale_pattern_manual(values = "stripe", name = "Clutter affected") +
  coord_sf(expand = FALSE) +
  facet_wrap(~fct_relevel(season, "Spring", "Autumn")) +
  annotation_scale(text_col = "black", style = "ticks", line_col = "black") +
  theme(panel.spacing.x = unit(0, "lines"),
        legend.position = "bottom", 
        legend.key.width = unit(1.5, "cm"))
ggsave("data/final_maps_plots/maps_raw.pdf", width = 17, height = 10, device = cairo_pdf)
```
## Small NL map

```{r}
ggplot() +
  geom_sf(data = rmapshaper::ms_simplify(nl, keep = 0.07), 
          fill = "white", color = "grey20", linewidth = 0.4) +
  geom_sf(data = st_buffer(radars, 35000), fill = "NA", color = "grey20", linewidth = 0.4) +
  geom_sf(data = radars, fill = "NA",  color = "black", size = 1) +
  theme_void()

ggsave(filename = "nl_tiny.pdf", width = 1.75, height = 2)
```

## Differences between 2.5hrs and 4hrs

```{r}
ban_dens_2h30 <- rast("data/final_maps/NL_autumn_night_thresh_250_s_4_n_25_2h30m.tif")
bsn_dens_2h30 <- rast("data/final_maps/NL_spring_night_thresh_250_s_4_n_25_2h30m.tif")

ban_dens_4h <- rast("data/final_maps/NL_autumn_night_thresh_250_s_4_n_25_4h00m.tif")
bsn_dens_4h <- rast("data/final_maps/NL_spring_night_thresh_250_s_4_n_25_4h00m.tif")

ban_2h30 <- ban_dens_2h30 / global(ban_dens_2h30, mean, na.rm = TRUE)[[1]]
ban_4h <- ban_dens_4h / global(ban_dens_4h, mean, na.rm = TRUE)[[1]]

difban <- ban_2h30 - ban_4h

difban %>%
  as.data.frame() %>%
  ggplot() +
  geom_raster(aes(x = x, y = y, fill = focal_mean), data = difban) +
  scale_fill_gradientn(colours=coolwarm(100), limits = c(-1, 1))

bsn <- bsn / global(bsn, mean, na.rm = TRUE)[[1]]
```


